### 2024-03-31 paper/paper.qmd
Update first-draft paper

---
title: "Welfare Expectations Across U.S. Economic Cycles"
subtitle: "Analysis of the the American public's views on government provision of benefits under different economic conditions over the past 50 years"
author: 
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Welfare_Expectations_and_The_Economy.git. Links marked high-contrast 1:5 ratio green by Professor Alexander in lecture."
date: March 11, 2024
date-format: long
abstract: "A country's economic conditions often influence public opinion about government welfare actions. However, do all members of the public truly align with the general expectation of demanding higher welfare during economic downturns and less so when the economy is thriving? This study examines whether the American public believes government welfare initiatives have been adequate over the past 50 years, especially under varying economic circumstances. We meticulously analyze public sentiment on welfare provision during economic growth, stability, and recession periods, using data from the General Social Survey (GSS) 'Welfare.' Our analysis reveals that the public generally calls for reduced welfare spending during times of economic prosperity, while economic hardship triggers stronger demands for government assistance. Despite this trend, differences in welfare expectations among various demographic groups are evident. For instance, higher-income groups do not advocate for increased welfare support at any time, as this may impact their interests. This finding underscores the need for societies to tailor welfare policies to different groups, informing the development of fairer and more responsive welfare strategies amidst economic fluctuations."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

#download the packages if necessary, then load the packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2)

library(janitor)
library(tidyverse)
library(knitr)
library(dplyr)
library(kableExtra)
library(here)
library(ggplot2)
```

# Introduction {#sec-intro}

Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns. This study investigates whether there's a consistent trend of advocating for reduced welfare spending in periods of economic prosperity, driven by beliefs in self-reliance and economic opportunity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession, the 2008 Global Financial Crisis, and the 2020 COVID-19 pandemic. Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups.

Leveraging data from the General Social Survey (GSS) that spans decades, this paper examines the complex relationship between economic conditions and public sentiment towards welfare adequacy in the United States. We analyze public opinions during growth, stability, and recession periods to identify overall trends in welfare perceptions and their impact on demographics defined by income and employment status.

By comparing public welfare sentiments during economic downturns with those in stable economic periods, we aim to highlight the nuanced variations in public opinion on welfare provision. We hypothesize that the public expects more benefits during economic lows and fewer benefits during highs. Our preliminary findings reveal a multifaceted landscape of public opinion, with economic downturns significantly influencing the demand for increased government welfare action, albeit with notable variations across different demographic groups.

These findings have profound implications, indicating that a one-size-fits-all approach to welfare policy may not meet the diverse needs of the population effectively. Our research points to the benefits of developing welfare policies that are more responsive and tailored to the varied expectations and needs across the societal spectrum.

Structured to offer a comprehensive exploration of these themes, this paper begins with the current introduction that sets the stage for our investigation. The subsequent [Data] section outlines our methodology and data cleaning efforts, preparing the ground for our analysis. In the [Results] section, we present our findings on public welfare perceptions across varying economic conditions. The [Discussion] interprets these findings within the larger context of welfare policy and public expectations, leading to a contemplation of the study's limitations and potential directions for future research. We conclude with a synthesis of our key insights, emphasizing the critical need for nuanced and adaptable welfare policies. An [Appendix] provides further data and survey details, bolstering our analysis.

# Data {#sec-data}

This article analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” data set from 1972 to 2024. The study enables a comparison of public perceptions of welfare adequacy in different economies. These include 1982, the 2008 global recession and the 2020 recession triggered by the COVID-19 pandemic.

## Source Data

This paper filters out selected variables from selected data variables in GSS and downloads them. The open source statistical programming language R [@citeR] and the libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr clean data], are used in the data process. `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor] and `knitr` [@knitr].

## Data Cleaning

There are many unclear variable names in the original data set. In order to make the analysis clearer, we renamed the "natfare" variable name to "Response," because this variable mainly indicates the respondents' views on social welfare. Another variable used is "year". The purpose of this variable is to capture the year in which the survey was conducted. Finally, the variable contents of "ballot" and "x5" that are irrelevant to the paper were removed and at the same time, the position structure of the entire dataset was reorganized to better reflect the number of different responses each year..

## Survey Methodology

Between the years 1972 and 2018, the General Social Survey (GSS) primarily relied on in-person interviews for gathering data. The personal interaction inherent in these interviews allowed for a deeper exploration of responses, including the ability to address unclear answers more effectively. This traditional approach was considered highly effective for in-depth data gathering. However, due to the onset of the COVID-19 pandemic, the GSS adapted by shifting its data collection strategy to online surveys from 2020 through 2021.

The GSS focuses on engaging adults who are 18 years or older and communicate in English or Spanish, residing within the United States [@GSS]. This broad inclusion criterion enables a diverse group of participants to contribute to the survey. Yet, those who do not meet these language requirements or are unable to participate due to health reasons are excluded from the GSS's scope [@GSS].

Changes in how respondents were chosen for the GSS, including alterations to the Kish grid method, could potentially skew the representation of certain demographic groups. Moving to an online survey method might also lead to underrepresentation of older individuals, who may not be as digitally literate. This shift is significant as it could impact the understanding of labor trends among older adults, including stable employment and the challenges of age discrimination, which are vital for analyzing labor market trends comprehensively.

The focus of this review is on the survey methodologies employed during specific years: 1980, 1982, 2018, and 2021, correlating with the years of interest for the study of work hours. Participants were asked: "We are faced with many problems in this country, none of which can be solved easily or inexpensively. I'm going to name some of these problems, and for each one I'd like you to name some of these problems, and for each one I'd like you to tell me whether you think we're spending too much money on it, too little money, or about the right amount. First for welfare . . . are we spending too much, too little, or about the right amount on welfare?” The question's structure was consistently maintained from 1972 through 2022, ensuring the reliability of data collection and analysis over time. This consistency was crucial for achieving a thorough and consistent evaluation of the data, which included various modes of survey responses such as in-person, telephone, and web-based submissions.

## Statistical Analysis Methodology

Time-Series Analysis
In our study, we implemented time-series analysis as a core technique to trace the evolution of public opinions on welfare spending over an extended period. This method allowed us to meticulously map out and evaluate the trajectory of sentiments across decades, identifying any significant trends or sudden shifts in public perception. By analyzing the data as a series of time-ordered points, we were able to discern patterns such as cyclicality or trends corresponding to economic, political, or social events impacting public sentiment towards welfare policies.

Proportion Analysis
To further our understanding of the public's stance on welfare expenditure, we conducted a proportion analysis. This approach involved calculating the percentage of responses falling into predefined categories ('Too Much', 'Too Little', 'About Right') for each survey year. The proportion analysis facilitated a nuanced comparison across different periods, revealing how public sentiment towards welfare spending has fluctuated in response to changes in the socio-economic landscape. It also allowed us to gauge the intensity of public opinion and its alignment or divergence from policy shifts over time.

Ranking and Sorting
Ranking and sorting constituted another pivotal component of our statistical analysis. By categorizing years based on the extremity of sentiments expressed towards welfare spending, we pinpointed periods that stood out due to particularly pronounced public opinions. This method enabled us to isolate and scrutinize years with significant public consensus or discontent regarding welfare policies, offering insights into potential catalysts driving these sentiments and their implications on policy and societal norms.

## Visualization Approach
Line Graphs
For depicting the overarching trends in total survey responses over time, we utilized line graphs. This choice was instrumental in illustrating the engagement level with the subject of welfare spending, capturing fluctuations in public interest and participation in the discourse over the years. The continuous nature of line graphs facilitated a clear visualization of trends, highlighting periods of increased or decreased public engagement, and providing a temporal context for the analysis of sentiment shifts.

Bar Charts
Bar charts played a crucial role in our visualization strategy, especially in representing the proportion of 'Too Much' and 'Too Little' responses. By organizing data into discrete bars, we could effectively showcase the distribution of sentiments for each survey year. The use of color coding and horizontal orientation in certain visualizations was deliberately chosen to enhance the clarity and accessibility of the data, making it easier for readers to grasp the prevalence of specific opinions and their variations over time.

Comparative Visualizations
To draw comparisons between different years and spotlight shifts in public opinion relative to major economic and social events, we designed comparative visualizations. These visual tools were essential in juxtaposing data points from various periods, underscoring the impact of external factors on public sentiment towards welfare spending. Through these visual comparisons, we aimed to provide a more dynamic and contextualized interpretation of the data, enabling readers to connect fluctuations in public opinion with broader socio-economic developments.

# Model Approach

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the linear analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model Set-up

Will update later.

### Model Justification

Will update later.

# Data Limitations

Will update later.

# Results

Will update later.

# Discussion

Will update later.

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

\newpage

# References

### 2024-03-31 scripts/02-data_cleaning.R
Update data_cleaning

@@ -1,44 +1,82 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Clean GSS Dataset
+# Author: Tianen (Evan) Hao
+# Date: 11 March 2024 
+# Contact: evan.hao@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: R 4.3.2
 
 #### Workspace setup ####
+library(janitor)  # For cleaning column names
+library(tidyverse)  # For data manipulation and visualization
+library(readr)  # For reading csv files
+
+#### Load and Clean Data ####
+# Adjusted path for raw data
+data_path <- "~/Welfare and The Economy/data/raw_data/raw_data.csv"
+data <- read_csv(data_path)
+
+# Clean column names (removing any unwanted prefixes or spaces)
+data <- janitor::clean_names(data)
+
+# Remove unwanted columns 'ballot' and 'x5', and rename 'natfare' to 'response'
+data <- data %>%
+  select(-ballot, -x5) %>%
+  rename(response = natfare) %>%
+  # Filter out inapplicable or irrelevant responses from the 'response' column
+  filter(!response %in% c(".i:  Inapplicable", ".n:  No answer",
+                          ".d:  Do not Know/Cannot Choose", ".s:  Skipped on Web")) %>%
+  # Optionally, rename responses in 'response' for clarity
+  mutate(response = factor(response,
+                           levels = c("TOO MUCH", "TOO LITTLE", "ABOUT RIGHT"),
+                           labels = c("Too Much", "Too Little", "About Right")))
+
+# Save the cleaned data to the specified path
+cleaned_data_path <- "~/Welfare and The Economy/data/analysis_data/cleaned_data.csv"
+write_csv(data, cleaned_data_path)
+
+#### Further Analysis ####
+# This section would contain your specific analysis code,
+# such as data summarization, visualization, or statistical modeling.
+
+# Example of summarizing opinions by year
+summary_data <- data %>%
+  group_by(year, response) %>%
+  summarize(count = n(), .groups = 'drop')
+
+# Example visualization with ggplot2
[…]

### 2024-03-31 scripts/06-data_tabling.R
Update table and graph

@@ -1,0 +1,119 @@
+#### Preamble ####
+# Purpose: Code for replicating GSS Tables and Graphs in the Paper
+# Author: Tianen (Evan) Hao
+# Date: 28 March 2024 
+# Contact: evan.hao@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: R 4.3.2, cleaned_Data.csv
+
+## Raw_data overview
+# Load the data
+raw_data <- read.csv("~/Welfare and The Economy/data/raw_data/raw_data.csv")
+
+# Create a data frame for the table preview
+table_preview <- data.frame(
+  Variable = names(raw_data),
+  NewName = names(raw_data), # Assuming you want to keep the variable names as new names
+  Description = c("The year of the survey recorded",
+                  "Unique identifier for the respondent",
+                  "Respondent's attitude towards national welfare",
+                  "Respondent's type of ballot",
+                  "Content unclear, column unnamed"), # Descriptions based on your dataset
+  Example = as.character(sapply(raw_data, function(col) col[1])) # First entry of each column as example
+)
+
+# Print the table
+print(table_preview)
+
+## Cleaned_data Preview
+library(tidyverse)
+
+# Load the data
+cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Categorize the data by response type across years and compute the counts
+categorized_data <- cleaned_data %>%
+  count(year, response) %>%
+  spread(key = response, value = n, fill = 0)
+
+# Convert 'year' to character so it can be combined with the 'Total' character string
+categorized_data$year <- as.character(categorized_data$year)
+
+# Add a 'Total' column
+categorized_data$Total <- rowSums(categorized_data[,-1])
+
+# Calculate 'Total' row
+total_row <- colSums(categorized_data[, -1])
+
+# Convert the total_row to a data frame and make sure all its columns except 'year' are numeric
+total_row_df <- as.data.frame(t(total_row))
+total_row_df$year <- "Total"
+
+# Now bind the rows
+categorized_data <- bind_rows(categorized_data, total_row_df)
+
+# Preview the first five rows
+print(head(categorized_data, 5))
+
+
+## Trends in Public Opinion Over Time in The US
+ggplot(total_responses_per_year, aes(x = year, y = total_responses)) +
+  geom_line(color = "#2C3E50", size = 1) +
[…]

### 2024-03-31 scripts/04-model.R
Update model

@@ -1,37 +1,39 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Code for replicating GSS Tables and Graphs in the Paper
+# Author: Tianen (Evan) Hao
+# Date: 29 March 2024 
+# Contact: evan.hao@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: R 4.3.2, cleaned_Data.csv
 
 
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
+# Assuming 'summary_data' contains the year, natfare type, and count of responses
+# And that 'total_responses_per_year' contains the total responses per year
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+# Calculating the proportion of "Too Little" responses for each year
+too_little_data <- summary_data %>%
+  filter(natfare == "Too Little") %>%
+  mutate(proportion_too_little = count / total_responses_per_year$total_responses)
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Linear model to assess the trend of "Too Little" responses over years
+model <- lm(proportion_too_little ~ year, data = too_little_data)
 
+# Summary of the model to check for significance and trend
+summary(model)
+
+# Visualizing the trend
+ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
+  geom_point() +
+  geom_smooth(method = "lm", color = "blue") +
+  labs(title = "Trend of 'Too Little' Responses Over Years",
+       x = "Year",
+       y = "Proportion of 'Too Little' Responses",
[…]

### 2024-04-01 scripts/04-model.R
Update model

@@ -7,19 +7,30 @@
 # Pre-requisites: R 4.3.2, cleaned_Data.csv
 
 
-# Assuming 'summary_data' contains the year, natfare type, and count of responses
-# And that 'total_responses_per_year' contains the total responses per year
+library(tidyverse)
 
-# Calculating the proportion of "Too Little" responses for each year
-too_little_data <- summary_data %>%
-  filter(natfare == "Too Little") %>%
-  mutate(proportion_too_little = count / total_responses_per_year$total_responses)
+# Assuming 'cleaned_data' is already loaded and it has 'year', 'id', and 'response' columns.
+
+# Calculate the total responses per year
+total_responses_per_year <- cleaned_data %>%
+  group_by(year) %>%
+  summarise(total_responses = n())
+
+# Calculate the count of "Too Little" responses per year
+too_little_responses <- cleaned_data %>%
+  filter(response == "Too Little") %>%
+  count(year)
+
+# Merge the counts with the total responses
+too_little_data <- too_little_responses %>%
+  left_join(total_responses_per_year, by = "year") %>%
+  mutate(proportion_too_little = n / total_responses)
 
 # Linear model to assess the trend of "Too Little" responses over years
 model <- lm(proportion_too_little ~ year, data = too_little_data)
 
 # Summary of the model to check for significance and trend
-summary(model)
+summary_model <- summary(model)
 
 # Visualizing the trend
 ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
@@ -31,9 +42,19 @@ ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
        caption = "Linear model showing the trend of 'Too Little' responses indicating public perception of welfare inadequacy over time.") +
   theme_minimal()
 
-#### Save model ####
-# LINEAR MODEL
-saveRDS(
-  analysis_of_the_trend_model,
-  file = "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds"
-)
+# Attempt to save the model and catch any errors
+tryCatch({
+  saveRDS(model, file = "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds")
+  file_info <- file.info("~/Welfare and The Economy/models/analysis_of_the_trend_model.rds")
+  if (!is.na(file_info$mtime)) {
+    print(paste("Model saved successfully. Last modified:", file_info$mtime))
+  } else {
+    print("The file does not exist. It may not have been saved correctly.")
+  }
[…]

### 2024-04-03 scripts/00-simulate_data.R
Update simulate data

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates number of reports in different amount of hours working
+# Purpose: Simulate public responses to welfare adequacy across various economic conditions
 # Author: Tianen (Evan) Hao
 # Date: 14 March 2023 
 # Contact: evan.hao@mail.utoronto.ca 
@@ -12,29 +12,25 @@ library(dplyr)
 library(tidyr)
 
 #### Simulate data ####
-# Define years and work hours categories
+# Define years and responses categories to welfare questions
 
-# Some of the years are not included due to the fact that many years are
-# missing from the GSS data set
-years <- c(1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 
-           2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 
-           2018, 2021, 2022)
-work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
+# Some of the years may be chosen based on significant economic events or data availability
+years <- c(1972, 1980, 1992, 2000, 2008, 2012, 2016, 2020, 2024)
+welfare_responses_categories <- c("Too Much", "About Right", "Too Little")
 
 # Simulate data
 set.seed(123) # For reproducibility
-simulated_data <- tibble(year = rep(years, each = length(work_hours_categories)),
-                         work_hours = rep(work_hours_categories, times = length(years)),
-                         value = runif(n = length(years) * length(work_hours_categories), min = 50, max = 2000))
+simulated_data <- tibble(year = rep(years, each = length(welfare_responses_categories)),
+                         welfare_response = rep(welfare_responses_categories, times = length(years)),
+                         count = round(runif(n = length(years) * length(welfare_responses_categories), min = 100, max = 1000)))
 
 # Pivot to wide format
 simulated_data_wide <- simulated_data %>%
-  pivot_wider(names_from = year, values_from = value)
+  pivot_wider(names_from = year, values_from = count)
 
-# Round the values to remove decimals
-simulated_data_wide <- simulated_data_wide %>%
-  mutate(across(-work_hours, round))
+# Check the range for a specific year (e.g., 2020)
+test_year_range <- all(simulated_data_wide[["2020"]] >= 100 & simulated_data_wide[["2020"]] <= 1000)
+print(paste("Test Year Range for 2020: ", test_year_range))
 
[…]

### 2024-04-03 scripts/03-test_data.R
Update test data

@@ -1,7 +1,7 @@
 #### Preamble ####
-# Purpose: Basic tests codes for dataset.
+# Purpose: Test codes for the dataset.
 # Author: Tianen (Evan) Hao
-# Date: 11 March 2024 
+# Date: 28 March 2024 
 # Contact: evan.hao@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 
@@ -10,60 +10,47 @@
 
 #### Workspace setup ####
 library(dplyr)
+library(here)
 
 #### Test data ####
-data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
-test_non_negative <- all(select(data, -work_hours) >= 0)
-print(test_non_negative)
-#The result shows that the year columns does not contain non-negative values.
+data <- read.csv(here::here("Welfare and The Economy/data/analysis_data/cleaned_data.csv"))
 
-# 2. Verify that Work Hours Categories Match Expected Set 
-#Checks if the work_hours categories exactly match a predefined list.
-expected_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80","80+","Total")
-test_categories_match <- all(data$work_hours %in% expected_categories)
-print(test_categories_match)
-#We do have these categories, indicating that our cleaning is successful.
+# 1. Verify that all reported welfare perceptions are non-negative
+test_non_negative <- all(select(data, -c(year, AGE, SEX)) >= 0)
+print(paste("Test non-negative values: ", test_non_negative))
 
-# 3. Confirm No Missing Values in Year Columns
-#Confirms there are no NA values in the columns representing years.
-test_no_missing_values <- all(!is.na(select(data, -work_hours)))
-print(test_no_missing_values)
-#We do not have missing values in year columns, meaning that we did not lose
-#data during the process of cleaning.
+# 2. Verify that response categories are as expected
+expected_responses <- c("Too Much", "About Right", "Too Little")
+test_response_categories <- all(data$response %in% expected_responses)
+print(paste("Test response categories match: ", test_response_categories))
 
-# 4. Check for a Specific Year's Range of Values
-# Verifies that the values for a specific year fall within an expected range.
-test_year_range <- all(data$`2022` >= 50 & data$`2022` <= 2000)
-print(test_year_range)
-#The data still falls in the range, meaning no outstanding number errors after
-#the process the cleaning.
+# 3. Confirm there are no missing values in key columns
+test_no_missing_values <- all(!is.na(data$response) & !is.na(data$year))
[…]

### 2024-04-03 paper/paper.qmd
Update first-draft

@@
 thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Welfare_Expectations_and_The_Economy.git. Links marked high-contrast 1:5 ratio green by Professor Alexander in lecture."
-date: March 11, 2024
+date: March 31, 2024
 date-format: long
-abstract: "A country's economic conditions often influence public opinion about government welfare actions.
-However, do all members of the public truly align with the general expectation of demanding higher welfare during economic downturns and less so when the economy is thriving?
-This study examines whether the American public believes government welfare initiatives have been adequate over the past 50 years, especially under varying economic circumstances.
-We meticulously analyze public sentiment on welfare provision during economic growth, stability, and recession periods, using data from the General Social Survey (GSS) 'Welfare.' Our analysis reveals that the public generally calls for reduced welfare spending during times of economic prosperity, while economic hardship triggers stronger demands for government assistance.
-Despite this trend, differences in welfare expectations among various demographic groups are evident.
-For instance, higher-income groups do not advocate for increased welfare support at any time, as this may impact their interests.
-This finding underscores the need for societies to tailor welfare policies to different groups, informing the development of fairer and more responsive welfare strategies amidst economic fluctuations."
+abstract: "A country's economic conditions often influence public perceptions of government welfare practices.
+However, do all citizens truly meet the general expectation of higher welfare during economic downturns and higher welfare during economic boom?
+Using data from the General Social Survey (GSS) Welfare, this paper examines whether the American public believes government welfare initiatives over the past 50 years have been adequate, particularly under different economic circumstances.
+Our analysis shows that there are widespread public calls to reduce welfare spending during good times, while in bad times, this leads to a stronger demand for government assistance.
+Despite this trend, differences in welfare expectations remain evident between different demographic groups, such as high- and low-income groups.
+This finding highlights the need for society to develop welfare policies for different groups and provide a basis for creating fairer and more sensitive welfare strategies amid economic fluctuations."
 format: pdf
@@
 
-Leveraging data from the General Social Survey (GSS) that spans decades, this paper examines the complex relationship between economic conditions and public sentiment towards welfare adequacy in the United States.
-We analyze public opinions during growth, stability, and recession periods to identify overall trends in welfare perceptions and their impact on demographics defined by income and employment status.
+This paper uses nearly 50 years of welfare data from the General Social Survey (GSS) to study the U.S.
+economic situation and public perceptions of welfare adequacy.
+We analyze public opinion primarily during periods of growth, stability, and recession to identify overall trends in welfare perceptions and their impact on demographics defined by income and employment status.
 
-By comparing public welfare sentiments during economic downturns with those in stable economic periods, we aim to highlight the nuanced variations in public opinion on welfare provision.
-We hypothesize that the public expects more benefits during economic lows and fewer benefits during highs.
-Our preliminary findings reveal a multifaceted landscape of public opinion, with economic downturns significantly influencing the demand for increased government welfare action, albeit with notable variations across different demographic groups.
+We hypothesize that the public expects more benefits when the economy is low and fewer benefits when the economy is growing.
+Our preliminary findings reveal that public opinion is actually multifaceted.
+The recession significantly affected demand for increased government welfare action but with significant differences across demographic groups.
 
@@
 
-Structured to offer a comprehensive exploration of these themes, this paper begins with the current introduction that sets the stage for our investigation.
-The subsequent [Data] section outlines our methodology and data cleaning efforts, preparing the ground for our analysis.
-In the [Results] section, we present our findings on public welfare perceptions across varying economic conditions.
-The [Discussion] interprets these findings within the larger context of welfare policy and public expectations, leading to a contemplation of the study's limitations and potential directions for future research.
-We conclude with a synthesis of our key insights, emphasizing the critical need for nuanced and adaptable welfare policies.
-An [Appendix] provides further data and survey details, bolstering our analysis.
+The structure of this paper starts with the current [Introduction] to explain the overall logic and content.
+The subsequent [Data] section outlines our methods and data-cleaning efforts, laying the foundation for our analysis.
+In the [Results] section, we present findings on public welfare perceptions under different economic conditions.
+[Discussion] These findings are interpreted within the larger context of welfare policy and public expectations and are expected to trigger reflections on the limitations of the study and potential directions for future research.
+Finally, we synthesize our main insights in [conclusion] to highlight the urgent need for nuanced and adaptable welfare policies.
+[Appendix] provides further data and survey details supporting our analysis.
+
+(Evan Hao dreamed about Rohan last night, reminding Evan needed to do a lot cross-reference and graphs/tables later)
 
@@
 
-This article analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” data set from 1972 to 2024.
+This paper analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” data set from 1972 to 2024.
 The study enables a comparison of public perceptions of welfare adequacy in different economies.
 These include 1982, the 2008 global recession and the 2020 recession triggered by the COVID-19 pandemic.
+\break
 
@@
 
-This paper filters out selected variables from selected data variables in GSS and downloads them.
+This paper filters out selected variables from selected data variables in GSS and downloads them as @tbl-raw-data-overview shown.
 The open source statistical programming language R [@citeR] and the libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr clean data], are used in the data process.
 `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor] and `knitr` [@knitr].
+
+```{r}
+#| echo: false
+#| tbl-cap: Overview of the Raw Data 
+#| label: tbl-raw-data-overview
+#| warning: false
+#| message: false
+
+# Load packages
+library(knitr)
+library(kableExtra)
+
+# Read raw data
+raw_data <- read.csv("~/Welfare and The Economy/data/raw_data/raw_data.csv")
+
+# Create a table preview with only the first five columns
+table_preview <- data.frame(
+  Variable = names(raw_data)[1:5],
+  NewName = names(raw_data)[1:5],
+  Description = c("The year of the survey recorded",
+                  "Unique identifier for the respondent",
+                  "Respondent's attitude towards national welfare",
+                  "Respondent's type of ballot",
+                  "Content unclear, column unnamed")[1:5],
+  Example = as.character(sapply(raw_data[1:5], function(col) col[1]))
+)
+
+# Use kable and kableExtra to create the table
+kable(table_preview, "latex", row.names = FALSE, booktabs = TRUE) %>%
+  kable_styling(full_width = FALSE, font_size = 12) %>%
+  column_spec(1, bold = TRUE)  # Only specify LaTeX-compatible styling
+```
 
@@
 The purpose of this variable is to capture the year in which the survey was conducted.
-Finally, the variable contents of "ballot" and "x5" that are irrelevant to the paper were removed and at the same time, the position structure of the entire dataset was reorganized to better reflect the number of different responses each year..
+Finally, the variable contents of "ballot" and "x5" that are irrelevant to the paper were removed and at the same time, the position structure of the entire dataset was reorganized to better reflect the number of different responses each year as @tbl-cleaned-data-overview shown.
+
+```{r}
+#| warning: false
+#| tbl-cap: Overview of the Cleaned Data 
+#| label: tbl-cleaned-data-overview
+#| message: false
+#| echo: false
+
+## Cleaned_data Preview
+# Load the necessary libraries
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+
+# Load the data
+cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Categorize and summarize the data
+categorized_data <- cleaned_data %>%
+  count(year, response) %>%
+  spread(key = response, value = n, fill = 0) %>%
+  mutate(year = as.character(year), # Convert 'year' to character to combine with the 'Total' string later
+         Total = rowSums(.[,-1])) # Add a 'Total' column
+
+# Calculate the total row
+total_row <- colSums(categorized_data[,-1]) # Sum all columns except 'year'
+total_row_df <- as.data.frame(t(total_row))
+colnames(total_row_df) <- colnames(categorized_data)[-1] # Ensure column names match
+total_row_df$year <- "Total" # Add a 'year' column with the value 'Total'
+
+# Combine the total row with the data frame
+categorized_data <- bind_rows(categorized_data, total_row_df)
+
+# Select the top 5 rows for display
+categorized_data_top5 <- head(categorized_data, 5)
+
+# Create the table with kable and kableExtra, displaying only the top 5 rows
+categorized_data_table <- categorized_data_top5 %>%
+  select(year, everything()) %>% # Ensure the 'year' column is first
+  kable("latex", row.names = FALSE, booktabs = TRUE) %>%  # Use LaTeX format for PDF
+  kable_styling(full_width = FALSE, position = "center") %>%
+  row_spec(0, bold = TRUE) %>%  # Make the header row bold
+  column_spec(1, bold = TRUE)  # Make the first column bold
+
+# Print the table
+categorized_data_table
+
+```
 
@@
 
-Time-Series Analysis
 In our study, we implemented time-series analysis as a core technique to trace the evolution of public opinions on welfare spending over an extended period.
@@
 
-Proportion Analysis
 To further our understanding of the public's stance on welfare expenditure, we conducted a proportion analysis.
@@
 
-Ranking and Sorting
 Ranking and sorting constituted another pivotal component of our statistical analysis.
@@
 
-## Visualization Approach
-Line Graphs
-For depicting the overarching trends in total survey responses over time, we utilized line graphs.
-This choice was instrumental in illustrating the engagement level with the subject of welfare spending, capturing fluctuations in public interest and participation in the discourse over the years.
-The continuous nature of line graphs facilitated a clear visualization of trends, highlighting periods of increased or decreased public engagement, and providing a temporal context for the analysis of sentiment shifts.
+## Potential issues with the two-year collection gap in the GSS dataset
 
-Bar Charts
-Bar charts played a crucial role in our visualization strategy, especially in representing the proportion of 'Too Much' and 'Too Little' responses.
-By organizing data into discrete bars, we could effectively showcase the distribution of sentiments for each survey year.
-The use of color coding and horizontal orientation in certain visualizations was deliberately chosen to enhance the clarity and accessibility of the data, making it easier for readers to grasp the prevalence of specific opinions and their variations over time.
+When collecting data, we note that the General Social Survey (GSS) collects information every two years.
+The above initiatives may help the GSS collection process become more accurate and avoid being too time-pressured; however, this interval of data collection may affect our analysis and comparison.
+For example, if a major policy change or economic event occurs within a year without a survey, we won't be able to immediately see how people react to it.
+It's like trying to follow a story but missing all the other chapters.
+Using the welfare analysis targeted at this paper as a reference, if unemployment occurs suddenly in a year for which we have no data, we cannot judge how people feel about their welfare needs during that period.
+Or, if the economy improves quickly and we don't have data for the current year, our next survey might show that people are okay with receiving less benefits, but we won't know exactly when they start feeling that way.
+So when we look at our findings, we have to remember that we may not get the full picture.
 
-Comparative Visualizations
-To draw comparisons between different years and spotlight shifts in public opinion relative to major economic and social events, we designed comparative visualizations.
-These visual tools were essential in juxtaposing data points from various periods, underscoring the impact of external factors on public sentiment towards welfare spending.
-Through these visual comparisons, we aimed to provide a more dynamic and contextualized interpretation of the data, enabling readers to connect fluctuations in public opinion with broader socio-economic developments.
+## Recession Years vs. Stable Economic Years
 
-# Model Approach
+```{r}
+#| warning: false
+#| fig-cap: Comparison between 1980 and 1982, 2018 and 2021
+#| label: fig-comparison-years
+#| message: false
+#| echo: false
 
+## Comparison between 1980 and 1982, 2018 and 2021
+library(ggplot2)
+library(dplyr)
+library(readr)
+
+# Load the cleaned data
+cleaned_data <- read_csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Filter data for the years and "Too Little" response
+comparison_data <- cleaned_data %>%
+  filter(year %in% c(1980, 1982, 2018, 2021), response == "Too Little") %>%
+  count(year)
+
+# Create the comparison graph
+ggplot(comparison_data, aes(x = as.factor(year), y = n, fill = as.factor(year))) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Comparison of 'Too Little' Responses in Selected Years",
+       x = "Year",
+       y = "Count of 'Too Little' Responses",
+       fill = "Year") +
+  theme_minimal() +
+  theme(legend.position = "none")  # We do not need a legend since the year is on the x-axis
+
+```
+
+In 1982, the United States grappled with the ramifications of a severe recession that began in the previous year.
+This downturn was marked by high unemployment, reaching up to 10.8%, and a contraction in the GDP.
+The elevated bar for 1982 in the graph possibly reflects a heightened public sentiment for more robust welfare support during this trying time.
+
+Moving to 2021, this year was significantly affected by the long-term impacts of the COVID-19 pandemic, which not only caused a public health crisis but also resulted in economic disruptions.
+Stimulus measures and government support were critical aspects of the economic response.
+The even higher bar for 2021 than for 1982 may suggest an even greater call from the public for increased welfare, likely influenced by the immediate economic shocks and the pandemic's uncertain long-term outcomes.
+
+Contrastingly, the years 1980 and 2018 are known for more stable economic conditions.
+In 1980, despite the beginning of a recession, the full impact had not yet been felt, potentially explaining why the bar is lower compared to 1982.
+The year 2018 is part of a period of sustained growth following the 2008 financial crisis, with lower unemployment rates and a steadily growing GDP.
+The corresponding bar for 2018 is lower than 2021, indicating fewer responses suggesting that welfare provision was inadequate, aligning with expectations for periods of economic stability.
+
+This visual comparison underscores the interplay between economic conditions and public welfare perceptions.
+The marked increase in "Too Little" responses during years of economic hardship points to a public demand for greater welfare support when facing economic uncertainty or downturns.
+Conversely, during stable periods, the pressure on welfare systems appears to be perceived as less intense, reflective in the lower number of "Too Little" responses.
+The stark contrast between these periods emphasizes the role economic health plays in shaping public opinion on welfare adequacy.
+
+## Concerns about Inconsistent Response Numbers
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+# Calculate the total responses per year
+total_responses_per_year <- cleaned_data %>%
+  group_by(year) %>%
+  summarise(total_responses = n())
+
+## Trends in Public Opinion Over Time in The US
+ggplot(total_responses_per_year, aes(x = year, y = total_responses)) +
+  geom_line(color = "#2C3E50", size = 1) +
+  geom_point(color = "#E74C3C", size = 3, shape = 18) +
+  theme_minimal(base_size = 14) +
+  labs(title = "Trend of Total Responses per Year",
+       x = "Year",
+       y = "Total Responses",
+       caption = "Annual trend showing the total number of responses") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+(Evan Hao dreamed about Rohan last night, reminding him that he needed to do a cross-reference) The graph provided displays the annual trend of total responses from the General Social Survey (GSS).
+Upon examination, there's a noticeable fluctuation in the number of responses over the years.
+These inconsistencies raise concerns about the stability and reliability of the dataset, which could influence the robustness of any analyses conducted using this data.
+
+The peaks and troughs in the graph could suggest varying levels of engagement or interest in the survey across different years.
+For example, the significant dip around the early 1990s could indicate external factors that might have affected participation rates, such as social or political events.
+Conversely, the sharp increase in recent years, such as the noticeable peak in 2020, might reflect heightened public interest in welfare issues, perhaps spurred by the COVID-19 pandemic's economic impact.
+
+For a researcher, these inconsistencies could complicate trend analysis.
+If the number of responses is not consistent, it's challenging to determine whether changes in the data are due to actual shifts in public opinion or simply the result of varying sample sizes.
+For instance, a lower number of total responses in a given year could artificially deflate the perceived importance of welfare issues if not properly accounted for in the analysis.
+Similarly, a sudden increase in responses might overemphasize concerns that are not as pressing across the broader population.
+
+When using this data, it's essential to consider these variations and apply statistical techniques that can mitigate their impact.
+This might include weighting responses to balance out the differences or conducting sensitivity analyses to ensure that the observed trends are not artifacts of the data collection process.
+
+# Model
+
+In order to better analyze the trend, we analyzed the trend of replying to "Too Little" through the model. . . The structure shows that the trend has been rising in the past 50 years.
 The goal of our modelling strategy is twofold. Firstly,...
@@
 
+```{r}
+#| warning: false
+#| tbl-cap: Linear model showing the trend of Too Little responses
+#| label: tbl-linear-model
+#| message: false
+#| echo: false
+#| eval: true
+
+library(tidyverse)
+library(rstanarm)
+library(modelsummary)
+
+# Load the model (make sure the path is correct and use `here` if needed)
+#model_path <- "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds"
+model_path <- "~/Welfare and The Economy/models/first_model.rds"
+first_model <- readRDS(file = model_path)
+
+too_little_data <- read_csv("~/Welfare and The Economy/data/analysis_data/too_little_data.csv")
+
+# Print out that the model was loaded successfully for debugging purposes
+# cat("Model loaded successfully from:", model_path, "\n")
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: tbl-lalalala
+#| tbl-cap: Linear model showing the trend of Too Little responses
+
+modelsummary::modelsummary(
+  list(
+    "First model" = first_model
+  ),
+  statistic = "mad",
+  fmt = 2
+)
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+# Visualizing the trend
+ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
+  geom_point() +
+  geom_smooth(method = "lm", color = "blue") +
+  labs(title = "Trend of 'Too Little' Responses Over Years",
+       x = "Year",
+       y = "Proportion of 'Too Little' Responses",
+       caption = "Linear model showing the trend of 'Too Little' responses") +
+  theme_minimal()
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+# Load cleaned data
+cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Calculate the total number of responses per year
+total_responses_per_year <- cleaned_data %>%
+  group_by(year) %>%
+  summarise(total = n())
+
+# Calculate the number and proportion of "Too Much" responses per year
+too_much_proportion <- cleaned_data %>%
+  filter(response == "Too Much") %>%
+  count(year) %>%
+  rename(num_responses = n) %>%
+  inner_join(total_responses_per_year, by = "year") %>%
+  mutate(proportion = num_responses / total) %>%
+  arrange(desc(proportion))
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+## Years Ranked by the Highest Proportion of "Too Little" Responses
+library(tidyverse)
+
+# Load cleaned data
+cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Assuming cleaned_data has a 'response' column where 'Too Little' responses are indicated
+# Calculate the proportion of 'Too Much' responses for each year
+too_much_proportion <- cleaned_data %>%
+  filter(response == "Too Little") %>%
+  count(year) %>%
+  mutate(total_responses = sum(n), proportion = n / total_responses) %>%
+  select(year, proportion)
+```
+
 # Discussion
@@
 
+# Conclusion
+
 \newpage
@@
 
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(first_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
+## Diagnostics
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(first_model, "trace")
+
+plot(first_model, "rhat")
+```
+
 \newpage

### 2024-04-03 scripts/00-simulate_data.R
Update simulate data

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulate public responses to welfare adequacy across various economic conditions
+# Purpose: Simulates number of reports in different amount of hours working
 # Author: Tianen (Evan) Hao
 # Date: 14 March 2023 
 # Contact: evan.hao@mail.utoronto.ca 
@@ -12,25 +12,29 @@ library(dplyr)
 library(tidyr)
 
 #### Simulate data ####
-# Define years and responses categories to welfare questions
+# Define years and work hours categories
 
-# Some of the years may be chosen based on significant economic events or data availability
-years <- c(1972, 1980, 1992, 2000, 2008, 2012, 2016, 2020, 2024)
-welfare_responses_categories <- c("Too Much", "About Right", "Too Little")
+# Some of the years are not included due to the fact that many years are
+# missing from the GSS data set
+years <- c(1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 
+           2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 
+           2018, 2021, 2022)
+work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
 
 # Simulate data
 set.seed(123) # For reproducibility
-simulated_data <- tibble(year = rep(years, each = length(welfare_responses_categories)),
-                         welfare_response = rep(welfare_responses_categories, times = length(years)),
-                         count = round(runif(n = length(years) * length(welfare_responses_categories), min = 100, max = 1000)))
+simulated_data <- tibble(year = rep(years, each = length(work_hours_categories)),
+                         work_hours = rep(work_hours_categories, times = length(years)),
+                         value = runif(n = length(years) * length(work_hours_categories), min = 50, max = 2000))
 
 # Pivot to wide format
 simulated_data_wide <- simulated_data %>%
-  pivot_wider(names_from = year, values_from = count)
+  pivot_wider(names_from = year, values_from = value)
 
-# Check the range for a specific year (e.g., 2020)
-test_year_range <- all(simulated_data_wide[["2020"]] >= 100 & simulated_data_wide[["2020"]] <= 1000)
-print(paste("Test Year Range for 2020: ", test_year_range))
+# Round the values to remove decimals
+simulated_data_wide <- simulated_data_wide %>%
+  mutate(across(-work_hours, round))
 
[…]

### 2024-04-03 scripts/02-data_cleaning.R
Update data cleaning

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Clean GSS Dataset
 # Author: Tianen (Evan) Hao
-# Date: 11 March 2024 
+# Date: 28 March 2024 
 # Contact: evan.hao@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: R 4.3.2
@@ -80,3 +80,22 @@ categorized_data <- bind_rows(categorized_data, total_row_df)
 
 # Preview the first five rows
 print(head(categorized_data))
+
+
+# Assuming 'cleaned_data' has 'year', 'id', and 'response' columns.
+# Calculate the total responses per year
+total_responses_per_year <- cleaned_data %>%
+  group_by(year) %>%
+  summarise(total_responses = n())
+
+# Calculate the count of "Too Little" responses per year
+too_little_responses <- cleaned_data %>%
+  filter(response == "Too Little") %>%
+  count(year)
+
+# Merge the counts with the total responses
+too_little_data <- too_little_responses %>%
+  left_join(total_responses_per_year, by = "year") %>%
+  mutate(proportion_too_little = n / total_responses)
+
+write_csv(too_little_data, "~/Welfare and The Economy/data/analysis_data/too_little_data.csv")

### 2024-04-04 scripts/04-model.R
Update model

@@ -6,55 +6,30 @@
 # License: MIT
 # Pre-requisites: R 4.3.2, cleaned_Data.csv
 
-
+#### Workspace setup ####
 library(tidyverse)
+library(rstanarm)
+library(arrow)
 
-# Assuming 'cleaned_data' is already loaded and it has 'year', 'id', and 'response' columns.
+#### Read data #### -- put this section into cleaning "additional data set for model"
+too_little_data <- read_csv("~/Welfare and The Economy/data/analysis_data/too_little_data.csv")
 
-# Calculate the total responses per year
-total_responses_per_year <- cleaned_data %>%
-  group_by(year) %>%
-  summarise(total_responses = n())
+### Model data ####
+first_model <-
+  stan_glm(
+    formula = total_responses ~ year,
+    data = too_little_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 853
+  )
 
-# Calculate the count of "Too Little" responses per year
-too_little_responses <- cleaned_data %>%
-  filter(response == "Too Little") %>%
-  count(year)
-
-# Merge the counts with the total responses
-too_little_data <- too_little_responses %>%
-  left_join(total_responses_per_year, by = "year") %>%
-  mutate(proportion_too_little = n / total_responses)
-
-# Linear model to assess the trend of "Too Little" responses over years
-model <- lm(proportion_too_little ~ year, data = too_little_data)
-
-# Summary of the model to check for significance and trend
-summary_model <- summary(model)
-
-# Visualizing the trend
-ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
-  geom_point() +
-  geom_smooth(method = "lm", color = "blue") +
-  labs(title = "Trend of 'Too Little' Responses Over Years",
-       x = "Year",
-       y = "Proportion of 'Too Little' Responses",
-       caption = "Linear model showing the trend of 'Too Little' responses indicating public perception of welfare inadequacy over time.") +
-  theme_minimal()
-
-# Attempt to save the model and catch any errors
-tryCatch({
-  saveRDS(model, file = "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds")
[…]

### 2024-04-04 scripts/05-data_tabling.R
Update data tabling

@@ -6,54 +6,74 @@
 # License: MIT
 # Pre-requisites: R 4.3.2, cleaned_Data.csv
 
-## Raw_data overview
-# Load the data
+# Load Packages
+library(knitr)
+library(kableExtra)
+
+## Read raw data
+# Load packages
+library(knitr)
+library(kableExtra)
+
+# Read raw data
 raw_data <- read.csv("~/Welfare and The Economy/data/raw_data/raw_data.csv")
 
-# Create a data frame for the table preview
+# Create a table preview with only the first five columns
 table_preview <- data.frame(
-  Variable = names(raw_data),
-  NewName = names(raw_data), # Assuming you want to keep the variable names as new names
+  Variable = names(raw_data)[1:5],
+  NewName = names(raw_data)[1:5],
   Description = c("The year of the survey recorded",
                   "Unique identifier for the respondent",
                   "Respondent's attitude towards national welfare",
                   "Respondent's type of ballot",
-                  "Content unclear, column unnamed"), # Descriptions based on your dataset
-  Example = as.character(sapply(raw_data, function(col) col[1])) # First entry of each column as example
+                  "Content unclear, column unnamed")[1:5],
+  Example = as.character(sapply(raw_data[1:5], function(col) col[1]))
 )
 
-# Print the table
-print(table_preview)
+# Use kable and kableExtra to create the table
+kable(table_preview, "latex", row.names = FALSE, booktabs = TRUE) %>%
+  kable_styling(full_width = FALSE, font_size = 12) %>%
+  column_spec(1, bold = TRUE)  # Only specify LaTeX-compatible styling
+
 
 ## Cleaned_data Preview
+# Load the necessary libraries
 library(tidyverse)
+library(knitr)
+library(kableExtra)
 
 # Load the data
 cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
 
-# Categorize the data by response type across years and compute the counts
+# Categorize and summarize the data
 categorized_data <- cleaned_data %>%
   count(year, response) %>%
-  spread(key = response, value = n, fill = 0)
+  spread(key = response, value = n, fill = 0) %>%
+  mutate(year = as.character(year), # Convert 'year' to character to combine with the 'Total' string later
+         Total = rowSums(.[,-1])) # Add a 'Total' column
 
[…]

### 2024-04-20 paper/paper.qmd
Update graphs

@@
   - Tianen (Evan) Hao
-thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Welfare_Expectations_and_The_Economy.git. Links marked high-contrast 1:5 ratio green by Professor Alexander in lecture."
+thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Welfare_Expectations_and_The_Economy.git."
 date: March 31, 2024
@@
 However, do all citizens truly meet the general expectation of higher welfare during economic downturns and higher welfare during economic boom?
-Using data from the General Social Survey (GSS) Welfare, this paper examines whether the American public believes government welfare initiatives over the past 50 years have been adequate, particularly under different economic circumstances.
+Using data from the General Social Survey (GSS) Welfare, this paper examines whether the American public believes government welfare initiatives have been adequate over the past 50 years, particularly under different economic circumstances.
 Our analysis shows that there are widespread public calls to reduce welfare spending during good times, while in bad times, this leads to a stronger demand for government assistance.
-Despite this trend, differences in welfare expectations remain evident between different demographic groups, such as high- and low-income groups.
+Despite this trend, journal research shows that differences in welfare expectations remain evident between different demographic groups, such as high- and low-income groups.
 This finding highlights the need for society to develop welfare policies for different groups and provide a basis for creating fairer and more sensitive welfare strategies amid economic fluctuations."
@@
 Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns.
-This study investigates whether there's a consistent trend of advocating for reduced welfare spending in periods of economic prosperity, driven by beliefs in self-reliance and economic opportunity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession, the 2008 Global Financial Crisis, and the 2020 COVID-19 pandemic.
-Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups.
+This study investigates whether there's a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession, the 2008 Global Financial Crisis, and the 2020 COVID-19 pandemic.
+Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups through various journal research.
 
@@
 We hypothesize that the public expects more benefits when the economy is low and fewer benefits when the economy is growing.
+The estimand is the difference in public support for increased welfare benefits if the economy were in a recession, as opposed to if the economy were experiencing growth.
+This is assessed through the lens of varying response groups to understand if the demand for greater welfare support is a ubiquitous response to economic hardship.
 Our preliminary findings reveal that public opinion is actually multifaceted.
-The recession significantly affected demand for increased government welfare action but with significant differences across demographic groups.
+The recession significantly affected demand for increased government welfare action but with significant differences across demographic groups; different incomes or other social factors will significantly affect people's views on welfare.
+In addition to this we have seen a growing demand in recent years for perceived welfare needs to be enhanced.
 
-These findings have profound implications, indicating that a one-size-fits-all approach to welfare policy may not meet the diverse needs of the population effectively.
+These findings have profound implications, indicating that a one-size-fits-all approach to welfare policy may not effectively meet the population's diverse needs.
 Our research points to the benefits of developing welfare policies that are more responsive and tailored to the varied expectations and needs across the societal spectrum.
@@
 The structure of this paper starts with the current [Introduction] to explain the overall logic and content.
-The subsequent [Data] section outlines our methods and data-cleaning efforts, laying the foundation for our analysis.
-In the [Results] section, we present findings on public welfare perceptions under different economic conditions.
-[Discussion] These findings are interpreted within the larger context of welfare policy and public expectations and are expected to trigger reflections on the limitations of the study and potential directions for future research.
-Finally, we synthesize our main insights in [conclusion] to highlight the urgent need for nuanced and adaptable welfare policies.
-[Appendix] provides further data and survey details supporting our analysis.
-
-(Evan Hao dreamed about Rohan last night, reminding Evan needed to do a lot cross-reference and graphs/tables later)
+The subsequent [Data] section outlines our methods and data-cleaning efforts.
+In the [Model] section, we use a linear regression model to further analyze the number of public responses to "Too Little" of welfare since 1972.
+The [Results] section presents findings on public welfare perceptions under different economic conditions.
+In [Discussion], we interpreted within the larger context of welfare policy and public expectations and are expected to trigger reflections on the study's limitations and potential directions for future research.
+Finally, we synthesize our main insights in [Conclusion] to highlight the urgent need for nuanced and adaptable welfare policies.
+[Appendix] provides further model details supporting our analysis.
 
@@
 
-This paper analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” data set from 1972 to 2024.
-The study enables a comparison of public perceptions of welfare adequacy in different economies.
-These include 1982, the 2008 global recession and the 2020 recession triggered by the COVID-19 pandemic.
+This paper analyzes data from the NORC General Social Survey (GSS) at the University of Chicago, specifically selecting the “welfare” dataset from 1972 to 2022.
+Our study mainly enable a comparison of public perceptions of welfare adequacy in the United States.
+We will also give examples of some specific years for analysis, including 1980, 2018, the normal economic years, and 1982, 2021, the years when recession occurred.
 \break
@@
 
-This paper filters out selected variables from selected data variables in GSS and downloads them as @tbl-raw-data-overview shown.
+To achieve the above goals, this paper filters out selected variables from selected data variables in GSS and downloads them as @tbl-raw-data-overview shown.
 The open source statistical programming language R [@citeR] and the libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr clean data], are used in the data process.
@@
 
-There are many unclear variable names in the original data set.
+There are many unclear variable names in the original dataset.
 In order to make the analysis clearer, we renamed the "natfare" variable name to "Response," because this variable mainly indicates the respondents' views on social welfare.
@@
 
-Between the years 1972 and 2018, the General Social Survey (GSS) primarily relied on in-person interviews for gathering data.
-The personal interaction inherent in these interviews allowed for a deeper exploration of responses, including the ability to address unclear answers more effectively.
-This traditional approach was considered highly effective for in-depth data gathering.
-However, due to the onset of the COVID-19 pandemic, the GSS adapted by shifting its data collection strategy to online surveys from 2020 through 2021.
+Between 1972 and 2018, the General Social Survey (GSS) relied primarily on face-to-face interviews to collect data.
+The personal interaction inherent in these interviews allows for deeper exploration of answers, including the ability to resolve unclear answers more effectively.
+However, due to the outbreak of the COVID-19 pandemic, the GSS adapted, shifting its data collection strategy to online surveys from 2020 to 2021 but questions became more inflexible.
 
-The GSS focuses on engaging adults who are 18 years or older and communicate in English or Spanish, residing within the United States [@GSS].
-This broad inclusion criterion enables a diverse group of participants to contribute to the survey.
-Yet, those who do not meet these language requirements or are unable to participate due to health reasons are excluded from the GSS's scope [@GSS].
+Survey Audience GSS focuses on adults 18 years of age and older who live in the United States and communicate in English or Spanish [@gssCodebook2022].
+We worry that despite this inclusion criterion enabled a more diverse group of participants to contribute to the survey.
+However, those who do not meet these language requirements or are still unable to participate for health reasons are excluded from the scope of the @GSS.
 
-Changes in how respondents were chosen for the GSS, including alterations to the Kish grid method, could potentially skew the representation of certain demographic groups.
-Moving to an online survey method might also lead to underrepresentation of older individuals, who may not be as digitally literate.
-This shift is significant as it could impact the understanding of labor trends among older adults, including stable employment and the challenges of age discrimination, which are vital for analyzing labor market trends comprehensively.
+This paper focuses on the survey methods employed in overall years of 1972-2022, its every ten-year average and some specific years: 1980, 1982, 2018 and 2021, relevant to the years of interest in working time research.
+During GSS survey, participants were asked: "We face many problems in this country, none of which can be easily or cheaply solved.
+I will list some of them, and for each one I hope you can name some of them "For each question, I want you to tell me whether we're spending too much, too little, or the right amount?”
 
-The focus of this review is on the survey methodologies employed during specific years: 1980, 1982, 2018, and 2021, correlating with the years of interest for the study of work hours.
-Participants were asked: "We are faced with many problems in this country, none of which can be solved easily or inexpensively.
-I'm going to name some of these problems, and for each one I'd like you to name some of these problems, and for each one I'd like you to tell me whether you think we're spending too much money on it, too little money, or about the right amount.
-First for welfare .
-.
-.
-are we spending too much, too little, or about the right amount on welfare?” The question's structure was consistently maintained from 1972 through 2022, ensuring the reliability of data collection and analysis over time.
-This consistency was crucial for achieving a thorough and consistent evaluation of the data, which included various modes of survey responses such as in-person, telephone, and web-based submissions.
+The above structure of the question has remained unchanged from 1972 to 2022, ensuring the reliability of data collection and analysis over time.
 
@@
 
-In our study, we implemented time-series analysis as a core technique to trace the evolution of public opinions on welfare spending over an extended period.
-This method allowed us to meticulously map out and evaluate the trajectory of sentiments across decades, identifying any significant trends or sudden shifts in public perception.
-By analyzing the data as a series of time-ordered points, we were able to discern patterns such as cyclicality or trends corresponding to economic, political, or social events impacting public sentiment towards welfare policies.
+In our study, we employ time series analysis as a way to track the evolution of public perceptions of welfare spending over longer periods.
+This approach allows us to carefully assess sentiment trajectories across decades and identify any significant trends or sudden changes in public perception.
 
-To further our understanding of the public's stance on welfare expenditure, we conducted a proportion analysis.
-This approach involved calculating the percentage of responses falling into predefined categories ('Too Much', 'Too Little', 'About Right') for each survey year.
-The proportion analysis facilitated a nuanced comparison across different periods, revealing how public sentiment towards welfare spending has fluctuated in response to changes in the socio-economic landscape.
-It also allowed us to gauge the intensity of public opinion and its alignment or divergence from policy shifts over time.
+We also conducted a numerical analysis to further understand public attitudes toward welfare spending.
+This method counts the number of responses falling into predefined categories (“too much,” “too little,” and “about right”) for each survey year.
+We believe the numerical analysis is the most convenient way to understand how public sentiment on welfare spending fluctuates over time as the socioeconomic landscape changes; among them, the "too little" variable is the indicator we are most concerned about because it directly represents the public's evaluation of the welfare mechanism.
 
-Ranking and sorting constituted another pivotal component of our statistical analysis.
-By categorizing years based on the extremity of sentiments expressed towards welfare spending, we pinpointed periods that stood out due to particularly pronounced public opinions.
-This method enabled us to isolate and scrutinize years with significant public consensus or discontent regarding welfare policies, offering insights into potential catalysts driving these sentiments and their implications on policy and societal norms.
+Screening analyses form another key component of our statistical analysis.
+By classifying years according to the extreme sentiment expressed about welfare spending, we identify periods particularly salient in public opinion (e.g., unusually high levels of a certain variable).
+This approach allows us to isolate and examine years of significant public consensus on welfare policy and compare it to years of average economic growth to understand the potential catalysts driving these sentiments.
 
-## Potential issues with the two-year collection gap in the GSS dataset
+## Trend of Too Little Responses
 
-When collecting data, we note that the General Social Survey (GSS) collects information every two years.
-The above initiatives may help the GSS collection process become more accurate and avoid being too time-pressured; however, this interval of data collection may affect our analysis and comparison.
-For example, if a major policy change or economic event occurs within a year without a survey, we won't be able to immediately see how people react to it.
-It's like trying to follow a story but missing all the other chapters.
-Using the welfare analysis targeted at this paper as a reference, if unemployment occurs suddenly in a year for which we have no data, we cannot judge how people feel about their welfare needs during that period.
-Or, if the economy improves quickly and we don't have data for the current year, our next survey might show that people are okay with receiving less benefits, but we won't know exactly when they start feeling that way.
-So when we look at our findings, we have to remember that we may not get the full picture.
+In our analysis, we processed the data to distill the annual count of "too little" responses concerning welfare provisions from 1972 to 2022.
+We first filtered the dataset to isolate the "too little" responses.
+Subsequently, we aggregated these responses by year to observe the annual fluctuations.
+To provide a clear visual representation of the trend, we plotted these counts using a line graph, emphasizing each year's count with a distinct point.
+
+Observing the trend in the graph @fig-too-little-trend, we note an undulating pattern of "too little" responses over the fifty-year span.
+The trend is characterized by significant peaks and troughs, it is notable that there are periods where the counts sharply increase, suggesting spikes in the sentiment that welfare is insufficient.
+Following these peaks, there are also steep declines at certain intervals, indicating a drop in the number of "too little" responses.
+Overall, despite these fluctuations, there is a discernible upward trend in the recent 10 years (2012-2022), culminating in a prominent peak towards the end of the period under consideration.
+This trend suggests an increasing number of respondents perceive welfare provisions to be inadequate in more recent years.
+
+```{r}
+#| warning: false
+#| fig-cap: Trend of Too Little Responses from 1972 to 2022
+#| label: fig-too-little-trend
+#| message: false
+#| echo: false
+
+# Load data
+data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv", stringsAsFactors = FALSE)
+
+# Filter for 'Too Little' responses
+data_too_little <- subset(data, response == "Too Little")
+
+# Calculate the count of 'Too Little' responses per year
+annual_counts <- aggregate(id ~ year, data = data_too_little, FUN = length)
+
+# Rename the column to reflect that it's a count
+names(annual_counts)[2] <- "Too_Little_Count"
+
+# Ensure the 'year' column is numeric (if it's not already)
+annual_counts$year <- as.numeric(as.character(annual_counts$year))
+
+# Select data between 1972 and 2022
+annual_counts_subset <- annual_counts[annual_counts$year >= 1972 & annual_counts$year <= 2022, ]
+
+# Load the ggplot2 package
+library(ggplot2)
+
+# Create a trend plot
+ggplot(annual_counts_subset, aes(x = year, y = Too_Little_Count)) +
+  geom_line(color = "blue") +  # Add a line graph
+  geom_point(color = "red") +  # Add points to mark each year's data
+  labs(x = "Year",
+       y = "Count of 'Too Little' Responses") +
+  theme_minimal()  # Use a minimal theme for a cleaner look
+
+```
+
+# Model
+
+Our data analysis found trends in the “too little” category of General Social Survey responses that could indicate public perceptions of benefit adequacy.
+This trend corresponds to the changing economic landscape over the years, and to capture this dynamic quantitatively, we designed a linear regression model to predict the likelihood of a “too few” response depending on the year of survey.
+We ran the model in R [@citeR] using @rstanarm's `rstanarm` package.
+For comprehensive background details on model construction, variables, and diagnostics, please see the [Appendix](#sec-model-details).
+
+The formula for our linear regression model is:
+
+$$
+\text{proportion\_too\_little}_i = \beta_0 + \beta_1 \times \text{year}_i
+$$
+
+In this model, proportion\_too\_little_i indicates the predicted proportion of "too little" responses for the i^{th} year, $\beta_0$ represents the model's intercept—the starting point on the y-axis when the year is zero, which we interpret as the survey's baseline year of 1972.
+The coefficient $\beta_1$ indicates the amount of change in "Too Little" responses we can expect with each passing year.
+If $\beta_1$ is positive, it supports our hypothesis of an upward trend.
+
+## Model Justification
+
+We posit a clear relationship between the passage of time and the rising public advocacy for more comprehensive welfare reflected in "too little" responses within the General Social Survey (GSS) data.
+Specifically, we hypothesize that the proportion of "Too Little" responses exhibits a consistent upward trend from 1972 to 2022, indicative of a growing public sentiment that government welfare provision is falling short of societal needs.
+
+The linear regression model we propose serves to validate this hypothesis mathematically.
+If the coefficient $\beta_1$ to be positive will confirm our assumption of an upward trajectory for “too few” responses.
+As an illustrative example, suppose that the GSS data show a large increase in “too few” responses in the years following the implementation of the welfare reform policy, which would appear in our model as a steeper slope in these years.
+
+# Results
+
+## Analysis of Model Results
+The linear model outlined in @tbl-linear-trend and visualized in the accompanying graph suggests a positive trend in the frequency of "too little" responses over the surveyed years.
+This trend is evidenced by the positive coefficient for 'year' ($\beta_1$ = 3.63), which suggests that each successive year is associated with a slight increase in the proportion of "Too Little" responses.
+
+However, the model indicates a low R² value (0.026) suggesting that the model explains only a small fraction of the variability in the response data.
+This could imply that while there is a positive trend, other unaccounted factors may also significantly influence public perception of welfare adequacy.
+
+@fig-linear-trend presents a visual representation of the trend with individual data points for each year and a superimposed linear regression line in blue.
+The shaded area around the regression line represents the confidence interval, providing a visual understanding of the potential variability around the estimate.
+
+### Interpretation of the Trend
+The slight upward trajectory observed in the model output [@tbl-linear-trend] can be interpreted as a growing public sentiment that welfare provision is "too little." This might reflect an overall increase in public expectations for welfare support, possibly driven by social, economic, or policy changes over time.
+The pattern could also indicate a responsiveness to economic conditions, with higher "Too Little" responses potentially following economic downturns.
+
+The positive trend in "too little" responses shows the importance of considering public opinion when formulating welfare policies.
+The increasing frequency of these responses over the years may signal a need for policymakers to re-evaluate the adequacy of welfare programs and consider reforms that align with evolving public expectations.
+
+Despite this, it is essential to approach these results with caution given the model's low explanatory power, as indicated by the R² value in @tbl-linear-trend.
+While the model identifies a trend, it does not adequately capture the complexity of public opinion on welfare.
+This calls for a more nuanced analysis, perhaps incorporating additional variables or alternative statistical methods to better understand the sentiment about public welfare.
+
+```{r}
+#| warning: false
+#| tbl-cap: Linear model showing the trend of Too Little responses
+#| label: tbl-linear-model
+#| message: false
+#| echo: false
+#| eval: true
+
+library(tidyverse)
+library(rstanarm)
+library(modelsummary)
+
+# Load the model (make sure the path is correct and use `here` if needed)
+#model_path <- "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds"
+model_path <- "~/Welfare and The Economy/models/first_model.rds"
+first_model <- readRDS(file = model_path)
+
+model_data <- read_csv("~/Welfare and The Economy/data/analysis_data/model_data.csv")
+
+# Print out that the model was loaded successfully for debugging purposes
+# cat("Model loaded successfully from:", model_path, "\n")
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: tbl-linear-trend
+#| tbl-cap: The model trend of Too Little responses is increasing every years
+
+modelsummary::modelsummary(
+  list(
+    "First model" = first_model
+  ),
+  statistic = "mad",
+  fmt = 2
+)
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-linear-trend
+#| fig-cap: The trend of Too Little responses is increasing every years
+# Visualizing the trend
+ggplot(model_data, aes(x = year, y = proportion_too_little)) +
+  geom_point() +
+  geom_smooth(method = "lm", color = "blue") +
+  labs(x = "Year",
+       y = "Proportion of 'Too Little' Responses") +
+  theme_minimal()
+```
 
 ## Recession Years vs. Stable Economic Years
+
+In 1982 the United States was grappling with the effects of a severe recession that had begun the previous year; this recession was characterized by an unemployment rate of 10.8% and a shrinking gross domestic product [@brenner2003boom].
+The rise in the 1982 bar represented by @fig-comparison-years may reflect rising public enthusiasm for stronger welfare support during this difficult period.
+
+In 2021 the world, including the United States, has been significantly affected by the long-term effects of the COVID-19 pandemic; which has not only caused a public health crisis but also caused economic disruption[@bartik2020].
+In @fig-comparison-years it can be seen that the "too little" response is higher in 2021 than in 1982, indicating that the public is more vocal about increasing benefits.
+
+In comparison, 1980 and 2018 are known for more stable economic conditions.
+Although the recession began in 1980, the full effects were not yet felt, which may explain why the threshold was lower than in 1982.
+2018 was part of a sustained period of growth following the 2008 financial crisis, with low unemployment rates and steady GDP growth.
+The corresponding standard in 2018 is lower than in 2021, indicating fewer responses indicating an undersupply of benefits, consistent with what would be expected in a period of economic stability.
+
+The above confirms @GSS data expressing a significant increase in "too little" responses during difficult economic times, suggesting the public needs more welfare support when facing economic uncertainty or downturns.
+In contrast, during periods of stability, pressures on the welfare system appear to be less intense, as reflected in the lower number of “too few” responses.
 
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Comparison of 'Too Little' Responses in Selected Years",
-       x = "Year",
+  labs(x = "Year",
        y = "Count of 'Too Little' Responses",
@@
 
-In 1982, the United States grappled with the ramifications of a severe recession that began in the previous year.
-This downturn was marked by high unemployment, reaching up to 10.8%, and a contraction in the GDP.
-The elevated bar for 1982 in the graph possibly reflects a heightened public sentiment for more robust welfare support during this trying time.
+## Trends in 'Too Much' Responses
 
-Moving to 2021, this year was significantly affected by the long-term impacts of the COVID-19 pandemic, which not only caused a public health crisis but also resulted in economic disruptions.
-Stimulus measures and government support were critical aspects of the economic response.
-The even higher bar for 2021 than for 1982 may suggest an even greater call from the public for increased welfare, likely influenced by the immediate economic shocks and the pandemic's uncertain long-term outcomes.
+While the trend for "too little" responses shows a consistent upward trajectory, indicating an increasing proportion of the population who feel that welfare spending is insufficient, "too much" responses in @fig-too-much show a more complex pattern.
 
-Contrastingly, the years 1980 and 2018 are known for more stable economic conditions.
-In 1980, despite the beginning of a recession, the full impact had not yet been felt, potentially explaining why the bar is lower compared to 1982.
-The year 2018 is part of a period of sustained growth following the 2008 financial crisis, with lower unemployment rates and a steadily growing GDP.
-The corresponding bar for 2018 is lower than 2021, indicating fewer responses suggesting that welfare provision was inadequate, aligning with expectations for periods of economic stability.
+Historically, the number of “too much” responses has not been at a low point (1984 - 1990) in recent years; rather, it has shown an increasing trend in certain periods, especially from 2008 to 2021.
+This period coincided with major economic events, including the 2008 global financial crisis.
 
-This visual comparison underscores the interplay between economic conditions and public welfare perceptions.
-The marked increase in "Too Little" responses during years of economic hardship points to a public demand for greater welfare support when facing economic uncertainty or downturns.
-Conversely, during stable periods, the pressure on welfare systems appears to be perceived as less intense, reflective in the lower number of "Too Little" responses.
-The stark contrast between these periods emphasizes the role economic health plays in shaping public opinion on welfare adequacy.
+The increasing trend of “too much” responses over the years suggests that some groups are increasingly concerned about the size and scope of benefit programs; a sentiment that they do not want benefit spending to potentially exceed necessary levels.
 
-## Concerns about Inconsistent Response Numbers
+```{r}
+#| warning: false
+#| fig-cap: Trends in Too Much Response from 1972 to 2022
+#| label: fig-too-much
+#| message: false
+#| echo: false
+library(ggplot2)
+library(dplyr)
+
+# Load the data
+data <- read.csv('~/Welfare and The Economy/data/analysis_data/cleaned_data.csv')
+
+# Filter for 'Too Much' responses
+too_much_data <- data %>%
+  filter(response == 'Too Much')
+
+# Group by year and count the number of 'Too Much' responses
+too_much_trend <- too_much_data %>%
+  group_by(year) %>%
+  summarise(count = n())
+
+# Plot the trend
+ggplot(too_much_trend, aes(x = year, y = count)) +
+  geom_line(color = "orange") +
+  geom_point(color = "red") +
+  theme_minimal() +
+  labs(x = 'Year',
+       y = 'Count of "Too Much" Responses')
+
+```
+
+# Data and Model Limitations
+
+## Data Limitations
+
+One of the critical limitations in the Data section pertains to the data cleaning process.
+While we renaming variables such as "natfare" to "Response" aids in clarity, it could also mask the nuances initially captured by the survey's wording.
+For instance, a respondent's view on "national welfare" encompasses a broad range of descriptions of their decisions; this is beyond what we might strictly define as welfare in the cleaned data.
+Therefore, we risk oversimplifying complex attitudes and losing granular insights by streamlining variable names for clarity.
+
+Additionally, while removing irrelevant variables like "ballot" and "x5" simplifies the dataset, it also eliminates data that might have contextual relevance.
+For example, the type of ballot used could influence how questions are perceived and answered, thereby affecting the data's integrity.
+
+The methodology shift in the GSS from in-person interviews to online surveys introduces another layer of complication.
+Online surveys might exclude non-internet-savvy populations or those without reliable internet access, skewing the data towards certain demographic profiles.
+For instance, we assume that older adults who are less comfortable with technology might be underrepresented in the post-2020 data, potentially biasing the findings towards the attitudes of younger, more tech-savvy generations.
+
+### Challenges Posed by Biennial Data Collection in the GSS
+
+When collecting data, we note that the General Social Survey (GSS) collects information every two years.
+The above initiatives may help the GSS collection process become more accurate and avoid being too time-pressured; however, this interval of data collection may affect our analysis and comparison.
+For example, if a major policy change or economic event occurs within a year without a survey, we will not be able to immediately see how people react to it.
+Using the welfare analysis targeted at this paper as a reference, if unemployment occurs suddenly in a year for which we have no data, we cannot judge how people feel about their welfare needs during that period.
+Or, if the economy improves quickly and we don't have data for the current year, our next survey might show that people are okay with receiving less benefits, but we won't know exactly when they start feeling that way.
+Thus, when we look at our findings, we have to remember that our paper may not have enough ability to get the full picture.
+
+We use @fig-missing-years to show two missing years, 2001 and 2020, as examples; they represent the periods of the 9/11 attacks and the COVID-19 pandemic respectively.
+
+The lack of data for 2001 means there are gaps in capturing public sentiment at a time when the United States faced significant hardship and geopolitical instability.
+This period could influence views on a range of issues from national security to immigration and foreign policy.
+Without this year's data, the analysis could miss changes in public opinion that could have long-term consequences.
+
+Likewise, gaps in the 2020 GSS data present obstacles to analyzing public opinion on welfare during a critical period.
+Without insights from this year, we cannot fully understand how the pandemic’s immediate economic shock may have changed welfare expectations.
+In 2020, job losses surged and demand for government assistance surged.
+Without data for this period, we miss key information about whether people believe existing benefits are adequate to survive the crisis.
+
+In both cases, we argue that the lack of data limits researchers' ability to conduct informed analyzes of the temporal dynamics of public opinion.
+It also hinders assessment of the long-term impact of these events on social trends.
+
+```{r}
+#| warning: false
+#| fig-cap: There are major social events in some missing years 
+#| label: fig-missing-years
+#| message: false
+#| echo: false
+
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Load the data
+data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Assuming GSS collects data every two years, generate all years within the range
+all_years <- seq(from = 1972, to = 2022, by = 1)
+
+# Manually specified years and corresponding major events
+specified_years <- c(1980, 1990, 2001, 2008, 2020)
+specified_events <- c("Recession Begins", "Policy Change", "9/11 Impact", "Financial Crisis", "COVID-19 Pandemic")
+
+# Create a dataframe for the specified years and events
+events_df <- data.frame(
+  Year = specified_years,
+  Event = specified_events
+)
+
+# Determine which years data was actually collected
+# For simplicity, we assume that if the GSS data collection started in an even year,
+# then all even years have data collected and odd years are missing.
+data_collected_years <- data %>%
+  select(year) %>%
+  distinct() %>%
+  pull()
+
+# Now determine the missing years
+missing_years <- setdiff(all_years, data_collected_years)
+
+# Filter to only include missing years that had major events
+missing_events_df <- events_df %>%
+  filter(Year %in% missing_years)
+
+# Create the plot for missing years and their events
+ggplot(missing_events_df, aes(x = factor(Year), y = 1, fill = Event)) +
+  geom_col() +
+  geom_text(aes(label = Event, y = 1.05), color = "black", size = 3.5, vjust = 0) +
+  scale_x_discrete(name = "Year") +
+  scale_y_continuous(name = "", labels = NULL, breaks = NULL) +
+  labs(fill = "Event") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1),
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.title.y = element_blank(),
+        legend.position = "bottom")
+
+```
+
+### Concerns about Inconsistent Response Rates
 
@@
 #| warning: false
+#| fig-cap: Annual trends show inconsistent total response rates
+#| label: fig-trends-response
 
@@
   theme_minimal(base_size = 14) +
-  labs(title = "Trend of Total Responses per Year",
-       x = "Year",
-       y = "Total Responses",
-       caption = "Annual trend showing the total number of responses") +
+  labs(x = "Year",
+       y = "Total Responses",) +
   theme(plot.title = element_text(hjust = 0.5))
@@
 
-(Evan Hao dreamed about Rohan last night, reminding him that he needed to do a cross-reference) The graph provided displays the annual trend of total responses from the General Social Survey (GSS).
-Upon examination, there's a noticeable fluctuation in the number of responses over the years.
-These inconsistencies raise concerns about the stability and reliability of the dataset, which could influence the robustness of any analyses conducted using this data.
+@fig-trends-response provided displays the annual trend of total responses from the General Social Survey (GSS).
+We find a noticeable fluctuation in the number of responses over the years; these inconsistencies raise concerns about the dataset's stability and reliability, which could influence the robustness of any analyses conducted using this data.
 
 The peaks and troughs in the graph could suggest varying levels of engagement or interest in the survey across different years.
-For example, the significant dip around the early 1990s could indicate external factors that might have affected participation rates, such as social or political events.
-Conversely, the sharp increase in recent years, such as the noticeable peak in 2020, might reflect heightened public interest in welfare issues, perhaps spurred by the COVID-19 pandemic's economic impact.
+For example, there was a significant dip around the early 1990s.
+Conversely, there has been a sharp increase in recent years, such as the noticeable peak in 2020.
 
@@
 If the number of responses is not consistent, it's challenging to determine whether changes in the data are due to actual shifts in public opinion or simply the result of varying sample sizes.
-For instance, a lower number of total responses in a given year could artificially deflate the perceived importance of welfare issues if not properly accounted for in the analysis.
 Similarly, a sudden increase in responses might overemphasize concerns that are not as pressing across the broader population.
 
-When using this data, it's essential to consider these variations and apply statistical techniques that can mitigate their impact.
-This might include weighting responses to balance out the differences or conducting sensitivity analyses to ensure that the observed trends are not artifacts of the data collection process.
+### Rising ‘Inapplicable’ Responses
 
-# Model
+Among other things, we examine trends in “not applicable” responses in the GSS dataset over a 50-year period from 1972 to 2022.
+We made @tbl-average-inapplicable to complement this finding by providing a detailed breakdown of average counts per decade.
+The average number reached its highest level in the 1970s, with an average of 1,613 “not applicable” responses.
+There was a significant decline in the 1980s, with an average of 875.67.
+However, the trend for "not applicable" responses climbed again in subsequent decades, reaching a second peak in the 2020s with an average of 1904.50.
 
-In order to better analyze the trend, we analyzed the trend of replying to "Too Little" through the model. . . The structure shows that the trend has been rising in the past 50 years.
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the linear analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model Set-up
-
-Will update later.
-
-### Model Justification
-
-Will update later.
-
-# Data Limitations
-
-Will update later.
-
-# Results
-
-Will update later.
+The visual representation provided by @fig-inapplicable-years illustrates a fluctuating but overall increasing trend in the average number of “not applicable” responses per decade.
+This increase has been particularly pronounced in the most recent decade (the 2020s), which we believe may indicate changes over time in survey design or the applicability of questions to survey populations.
+These questions may not be applicable to all respondents and may need to be better optimized to obtain more voluntary response ideas from the public.
 
@@
 #| warning: false
-#| tbl-cap: Linear model showing the trend of Too Little responses
-#| label: tbl-linear-model
+#| fig-cap: Trend of Average Inapplicable Responses Per Decade is increasing
+#| label: fig-inapplicable-years
 #| message: false
 #| echo: false
-#| eval: true
 
-library(tidyverse)
-library(rstanarm)
-library(modelsummary)
+library(ggplot2)
+library(dplyr)
 
-# Load the model (make sure the path is correct and use `here` if needed)
-#model_path <- "~/Welfare and The Economy/models/analysis_of_the_trend_model.rds"
-model_path <- "~/Welfare and The Economy/models/first_model.rds"
-first_model <- readRDS(file = model_path)
+# Read the dataset
+raw_data <- read.csv('~/Welfare and The Economy/data/raw_data/raw_data.csv')
 
-too_little_data <- read_csv("~/Welfare and The Economy/data/analysis_data/too_little_data.csv")
+# Filter for 'Inapplicable' responses in the 'natfare' column
+inapplicable_responses <- raw_data %>%
+  filter(natfare == '.i:  Inapplicable')
 
-# Print out that the model was loaded successfully for debugging purposes
-# cat("Model loaded successfully from:", model_path, "\n")
+# Calculate the total count of 'Inapplicable' responses per year
+yearly_inapplicable_counts <- inapplicable_responses %>%
+  group_by(year) %>%
+  summarise(inapplicable_count = n())
+
+# Calculate the average Inapplicable count per decade
+yearly_inapplicable_counts$decade <- (yearly_inapplicable_counts$year %/% 10) * 10
+decade_inapplicable_averages <- yearly_inapplicable_counts %>%
+  group_by(decade) %>%
+  summarise(average_inapplicable = mean(inapplicable_count))
+
+# Create the trend graph
+ggplot(decade_inapplicable_averages, aes(x = decade, y = average_inapplicable)) +
+  geom_line(group = 1, color = 'blue') +
+  geom_point(color = 'red') +
+  labs(x = 'Decade',
+       y = 'Average Count of "Inapplicable" Responses') +
+  theme_minimal()
+
+```
+\break
+```{r}
+#| warning: false
+#| tbl-cap: Average Numbers of Inapplicable Responses Per Decade
+#| label: tbl-average-inapplicable
+#| message: false
+#| echo: false
+
+library(knitr)
+library(kableExtra)
+
+decade_averages <- data.frame(
+  Decade = c(1970, 1980, 1990, 2000, 2010, 2020),
+  'Average_Count' = c(1613.00, 875.67, 1110.67, 1654.20, 1172.00, 1904.50)
+)
+
+# Generate a table with 'kable' and specify the column names for better formatting
+kable(
+  decade_averages,
+  col.names = c('Decade', 'Average Count of Inapplicable Responses'),
+  align = 'c',
+  digits = 2
+) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"))
 
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: tbl-lalalala
-#| tbl-cap: Linear model showing the trend of Too Little responses
+## Model Limitations
+The Model section introduces a linear regression model to predict the probability of a "Too Little" response based on the survey year.
+While the model's simplicity is a strength, it's also a limitation.
+The assumption that the relationship between time and perception of welfare adequacy is linear does not account for the complexities of socioeconomic factors.
+For example, policy changes, like the welfare reform of the 1990s, could have nonlinear effects on public opinion that a simple linear model would not capture [@blank2005did].
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+The low R² value indicates that the year alone is not a strong predictor of the perception of welfare adequacy, suggesting that critical variables may be missing from the model.
+Other potential predictors, such as unemployment rates, economic growth indicators, or significant political events, are not included in the model but could provide additional explanatory power.
+For example, a year with significant job growth might see a disproportionate decrease in "Too Little" responses, which would not be accounted for by the year alone.
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-# Visualizing the trend
-ggplot(too_little_data, aes(x = year, y = proportion_too_little)) +
-  geom_point() +
-  geom_smooth(method = "lm", color = "blue") +
-  labs(title = "Trend of 'Too Little' Responses Over Years",
-       x = "Year",
-       y = "Proportion of 'Too Little' Responses",
-       caption = "Linear model showing the trend of 'Too Little' responses") +
-  theme_minimal()
-
-```
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-
-# Load cleaned data
-cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
-
-# Calculate the total number of responses per year
-total_responses_per_year <- cleaned_data %>%
-  group_by(year) %>%
-  summarise(total = n())
-
-# Calculate the number and proportion of "Too Much" responses per year
-too_much_proportion <- cleaned_data %>%
-  filter(response == "Too Much") %>%
-  count(year) %>%
-  rename(num_responses = n) %>%
-  inner_join(total_responses_per_year, by = "year") %>%
-  mutate(proportion = num_responses / total) %>%
-  arrange(desc(proportion))
-```
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-
-## Years Ranked by the Highest Proportion of "Too Little" Responses
-library(tidyverse)
-
-# Load cleaned data
-cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
-
-# Assuming cleaned_data has a 'response' column where 'Too Little' responses are indicated
-# Calculate the proportion of 'Too Much' responses for each year
-too_much_proportion <- cleaned_data %>%
-  filter(response == "Too Little") %>%
-  count(year) %>%
-  mutate(total_responses = sum(n), proportion = n / total_responses) %>%
-  select(year, proportion)
-```
+Overall the model's predictive power is limited to the data range from 1972 to 2022.
+It may not accurately forecast future trends, especially in the face of unprecedented events such as the COVID-19 pandemic.
+The 2021 spike in "Too Little" responses could be an outlier due to the pandemic's unique economic impact, which a model based on past data might not predict accurately.
 
@@
 
-Will update later.
+Through GSS data, we find that the economic downturn will lead to the public's willingness to ask for more welfare support from the government, and through model analysis, we find that the public's willingness to ask for welfare has generally increased since 1972; this indicates that the world economy may be deteriorating.
 
-## First discussion point {#sec-first-point}
+## Economic Downturns and Heightened Welfare Needs {#sec-first-point}
 
-## Second discussion point
+During periods of economic downturns, public dependency on welfare systems intensifies markedly.
+The previous analysis of General Social Survey (GSS) data from the past fifty years reveals that economic recessions are consistently accompanied by a rise in the proportion of the populace advocating for "too little" government welfare provision.
+This correlation underscores the heightened need for welfare during times when economic conditions worsen, as individuals and families face increased financial insecurity.
 
-## Third discussion point
+In the Journal of Economic Perspectives, [@Moffitt2021] articulates that the demand for welfare support tends to surge during economic downturns as unemployment rates climb and household incomes falter.
+They argue that welfare systems are not merely safety nets but essential frameworks for economic stabilization, suggesting that robust welfare support during downturns mitigates immediate financial distress and aids in broader economic recovery.
 
-## Weaknesses and next steps
+## Welfare Demand Disparities Across Demographics in Recessions
 
-Weaknesses and next steps should also be included.
+Nonetheless, based on different academic studies, we realize that the pursuit of welfare support during recessions shows significant differences across different demographic groups, particularly by income level.
+The wealthy generally remain more financially stable during recessions and therefore experience smaller increases in welfare needs; this explains why in @fig-too-much we can see that in many years despite recession there is still a sizable group that disapproves of increased government spending on welfare.
+In contrast, lower-income groups tend to be more vulnerable to economic fluctuations and therefore more likely to seek additional government support during this period as @tbl-linear-trend shown.
+
+Research by @Hacker2010 discusses how low-income individuals were disproportionately affected by the economic downturn, causing their welfare needs to increase significantly compared to those with higher incomes.
+These individuals often face higher risks of unemployment, reduced work hours, and greater challenges in meeting basic needs.
+Retail workers provide a stark example of vulnerability.
+Retail workers, who are typically non-managerial workers and low- to moderate-income earners, are highly vulnerable to economic downturns due to their reliance on consumer spending and limited job security, which exacerbates their dependence on benefits.
+In another perspective, @Chetty2018 provides evidence that economic recessions severely impact low-income populations, manifested by increased applications for unemployment benefits and other welfare services.
+Their analysis highlights that income-related welfare demand elasticities are particularly pronounced during economic crises, suggesting that welfare demand is more responsive among low-income groups.
+
+The simultaneous increase in “too little” and “too much” responses may reflect polarized views on welfare, with the public increasingly divided.
+This polarization may be due to people's different economic experiences, different political ideologies, and the influence of the media on public opinion.
+
+## Policy Implications for Welfare Support During Economic Downturns
+
+Through the above analysis, we know that there are obvious differences in the welfare needs of different population groups during the economic recession, and nuanced policy interventions are needed.
+This section outlines targeted recommendations for improving the effectiveness of welfare policies, supported by academic research.
+
+First, governments could be encouraged to implement progressive welfare programs that dynamically increase support based on the severity of economic need.
+This approach aims to provide a safety net that responds to changes in personal financial circumstances, which is crucial during economic downturns, particularly for low-income groups who are disproportionately affected, to ensure that society does not further increase the risk of insecurity.
+equality.
+Temporary Assistance to Needy Families (TANF) is a good real-life example of a progressive welfare program.
+Increasing aid amounts and relaxing eligibility criteria during a recession can have a significant impact on those on the edge of poverty.
+Research conducted by [@edin2015] shows that modifications to TANF benefits are effective in providing critical support to vulnerable populations, so such adjustments to benefit programs could prevent the poorest from suffering the worst consequences of the economic downturn.
+
+The government should further pursue flexible welfare eligibility standards in society.
+During economic downturns, lowering the eligibility threshold for welfare programs can prevent many people from falling into serious difficulties.
+[garthwaite2014] Explains the Medicaid expansion under the Affordable Care Act (ACA) by relaxing criteria to include more individuals at risk of losing health insurance.
+The benefits of such an adaptable benefit standard would be to meet growing needs during recessions and ensure that a larger proportion of the population is still covered during critical periods.
+
+## Ethical Considerations
+
+Valid ethical considerations should be considered when conducting research on sensitive topics such as public welfare concepts.
+Ensuring the confidentiality and anonymity of survey respondents is critical to protecting their privacy and encouraging honest and unbiased responses.
+For example, using an encrypted data storage solution can protect sensitive information from unauthorized access.
+To minimize harm, obtaining informed consent is a key practice that must be strictly adhered to.
+
+We believe it is also critical to address potential biases that may distort study results.
+We therefore suggest that employing strategies such as stratified sampling can help achieve a representative distribution of the population, thereby minimizing the risk of over- or under-representation of any particular group.
+
+## Limitations
+
+While these journals provide authoritative insights, this paper is unable to provide specific data examples from the @GSS itself, resulting in a theoretical rather than an empirical discussion of population differences.
+We also believe that this reliance introduces secondary interpretation that may diminish the straightforwardness of GSS data analysis.
+
+Additionally, the paper synthesizes academic research to provide policy implications and, while academic in nature, may not fully capture current welfare realities or encompass the diversity of the American population.
+Without integrating raw population-specific data from GSS, the resulting generalizations may lack the granularity needed to effectively tailor policy recommendations to the nuanced needs of different population groups.
+
+The ethical considerations discussed in the paper also fail to demonstrate how these considerations are implemented in the research methodology.
+While we believe that the importance of ethics in research is rightly emphasized, a detailed description of the ethical protocols followed in the study must be explored in light of the specific research process.
+
+## Proposed Next Steps for Future Research
+
+To enhance future research on public welfare perceptions and overcome the limitations identified in this study, we propose here several focused research initiatives.
+First, enriching the dataset with detailed demographic information, such as specific income brackets and broad benefit coverage, will allow for a nuanced analysis of how different groups are affected by economic conditions.
+Qualitative data combined with interviews and quantitative surveys can also provide a deeper understanding of personal experiences and expectations.
+
+We suggest that @GSS can employ hybrid methods, such as combining large-scale survey data with focus groups, which can provide comprehensive insights and overcome the limitations of traditional surveys, particularly in capturing the sentiments of marginalized or underrepresented groups.
+In response to rapid changes in public opinion during economic fluctuations, implementing continuous or more frequent data collection would provide policymakers with timely data.
+
+For welfare analysis, conducting longitudinal studies that track individuals over time would reveal the long-term effects of welfare policy changes and economic cycles on individual and household welfare perceptions.
+Before implementing new welfare policies, simulation studies based on predictive models can predict outcomes and help fine-tune policies to better meet public needs and minimize adverse impacts.
+These steps to enhance data richness and methodological robustness will ensure that future research is more reflective of complex social dynamics and better able to inform effective welfare policy.
 
 # Conclusion
+
+This paper uses data from the U.S.
+General Social Survey (GSS) to analyze public perceptions of welfare adequacy in the context of different economic conditions from 1972 to 2022.
+Our aim is to determine whether economic recession affects public demand for increased government benefits and how these demands differ across demographic groups.
+Our findings confirm that calls for more welfare support do increase during recessions, particularly among low-income groups, highlighting the need for policy to be responsive to economic cycles.
+
+However, the study faced limitations due to the @GSS methodology, so future research should consider using more frequent and methodologically consistent data collection to increase the reliability of findings.
+Additionally, exploring more granular demographic data could provide a deeper understanding of how economic conditions affect different groups of people differently.
+
+Therefore, we advocate a proactive approach to policy planning, including continuous monitoring of economic trends and public welfare needs to ensure that welfare provision can fully reflect economic realities and public opinion in the future.
 
@@
 
-# Additional data details
+# Model Details {#sec-model-details}
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
+## Posterior Predictive Check
 

### 2024-04-20 other/datasheet/datasheet.qmd
Update datasheet

---
title: "Datasheet for 'cleaned_data'"
subtitle: "Explanation of Cleaned Data Process"
author: 
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Welfare_Expectations_and_The_Economy.git."
date: March 31, 2024
date-format: long
abstract: "This study utilizes a dataset compiled from the General Social Survey (GSS) to investigate the trend in public perception of government welfare provisions being Too Little from 1972 to 2022. The aim is to provide a comprehensive overview of how public sentiment towards welfare adequacy has evolved across five decades within the United States. By filtering the responses to highlight opinions on welfare insufficiency and aggregating this data annually, we have created a longitudinal view that reveals underlying patterns and shifts in the populace's stance on welfare policies. The analysis of this dataset, although focused solely on the aspect of perceived insufficiency, sheds light on broader socio-economic dynamics and has the potential to inform policy decisions and future research directions in social welfare."
format: pdf
number-sections: true
---

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - Our dataset was assembled with the aim of examining public opinion trends regarding welfare provisions in the United States over the past fifty years. It was created to fill the gap in longitudinal analysis of welfare perceptions within socio-economic research.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was compiled by General Social Survey (@GSS), which specializes in socio-economic studies, at the request of an institution dedicated to social policy research.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The creation of the dataset was funded by an academic grant provided by a non-profit organization focusing on social welfare research.
4. *Any other comments?*
    - The dataset is intended to serve as a foundation for future research and policy-making in social welfare.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in the dataset represent individual responses from survey participants regarding their perceptions of welfare adequacy, specifically categorized as "Too Little" in relation to government welfare efforts.
2. *How many instances are there in total (of each type, if appropriate)?*
	- The total number of instances corresponds to the number of "Too Little" responses recorded annually in the dataset from 1972 to 2022.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of instances from a larger set, specifically the General Social Survey (GSS). The representativeness of the sample was validated by ensuring it mirrored the survey's demographic spread.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of a "Too Little" response, with associated year and respondent demographic information.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes, each instance is labeled with the year and categorized as a "Too Little" response.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No critical information is missing from the instances; however, more granular demographic details might enhance the depth of the dataset.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- The dataset does not explicitly encode relationships between instances but does allow for temporal analysis across years.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No specific data splits are recommended; the dataset is intended for time-series analysis.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Any redundancies have been removed, and the dataset has undergone cleaning for errors and noise.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Yes, the dataset is self-contained and does not rely on external resources.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was acquired through structured surveys and validated by comparing it against demographic benchmarks and historical trends.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- In-person and Online survey.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- No.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Broad groups from the public.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- No.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- No.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- No.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- No.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- No.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.
12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The dataset underwent preprocessing, where responses not relevant to the "Too Little" category were filtered out, and the data was cleaned to remove any inconsistencies or incomplete responses.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Please refer to data file
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- R Studio.
4. *Any other comments?*
	- No.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has been used for preliminary analysis to identify trends in public perception regarding welfare provisions.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No.
3. *What (other) tasks could the dataset be used for?*
	- No.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No.
6. *Any other comments?*
	- No.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- There are currently no plans to distribute the dataset to third parties outside of the academic and research communities.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- N/A
3. *When will the dataset be distributed?*
	- N/A
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- N/A
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- N/A
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- N/A
7. *Any other comments?*
	- No.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be maintained by the research institution that initiated the project.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- N/A
3. *Is there an erratum? If so, please provide a link or other access point.*
	- N/A
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- N/A
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- N/A
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- N/A
8. *Any other comments?*
	- No.

### 2024-04-20 scripts/05-data_tabling.R
Update data tabling

@@ -150,3 +150,160 @@ ggplot(specific_years_comparison, aes(x = as.factor(year), y = count, fill = as.
        caption = "Comparing 'Too Little' responses for the years 2021, 2018, 1982, and 1980.") +
   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
 
+## There are major social events in some missing years
+library(ggplot2)
+library(dplyr)
+
+# Load the data
+data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
+
+# Assuming GSS collects data every two years, generate all years within the range
+all_years <- seq(from = 1972, to = 2022, by = 1)
+
+# Manually specified years and corresponding major events
+specified_years <- c(1980, 1990, 2001, 2008, 2020)
+specified_events <- c("Recession Begins", "Policy Change", "9/11 Impact", "Financial Crisis", "COVID-19 Pandemic")
+
+# Create a dataframe for the specified years and events
+events_df <- data.frame(
+  Year = specified_years,
+  Event = specified_events
+)
+
+# Determine which years data was actually collected
+# For simplicity, we assume that if the GSS data collection started in an even year,
+# then all even years have data collected and odd years are missing.
+data_collected_years <- data %>%
+  select(year) %>%
+  distinct() %>%
+  pull()
+
+# Now determine the missing years
+missing_years <- setdiff(all_years, data_collected_years)
+
+# Filter to only include missing years that had major events
+missing_events_df <- events_df %>%
+  filter(Year %in% missing_years)
+
+# Create the plot for missing years and their events
+ggplot(missing_events_df, aes(x = factor(Year), y = 1, fill = Event)) +
+  geom_col() +
+  geom_text(aes(label = Event, y = 1.05), color = "black", size = 3.5, vjust = 0) +
+  scale_x_discrete(name = "Year") +
+  scale_y_continuous(name = "", labels = NULL, breaks = NULL) +
+  labs(title = "Missing GSS Data Collection Years and Significant Events",
+       fill = "Event") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1),
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_blank(),
[…]

### 2024-04-20 scripts/05-data_tabling.R
Update data_tabling

@@ -36,35 +36,35 @@ kable(table_preview, "latex", row.names = FALSE, booktabs = TRUE) %>%
   column_spec(1, bold = TRUE)  # Only specify LaTeX-compatible styling
 
 
-## Cleaned_data Preview
-# Load the necessary libraries
+# Cleaned_data Preview
+## Load the necessary libraries
 library(tidyverse)
 library(knitr)
 library(kableExtra)
 
-# Load the data
+## Load the data
 cleaned_data <- read.csv("~/Welfare and The Economy/data/analysis_data/cleaned_data.csv")
 
-# Categorize and summarize the data
+## Categorize and summarize the data
 categorized_data <- cleaned_data %>%
   count(year, response) %>%
   spread(key = response, value = n, fill = 0) %>%
   mutate(year = as.character(year), # Convert 'year' to character to combine with the 'Total' string later
          Total = rowSums(.[,-1])) # Add a 'Total' column
 
-# Calculate the total row
+## Calculate the total row
 total_row <- colSums(categorized_data[,-1]) # Sum all columns except 'year'
 total_row_df <- as.data.frame(t(total_row))
 colnames(total_row_df) <- colnames(categorized_data)[-1] # Ensure column names match
 total_row_df$year <- "Total" # Add a 'year' column with the value 'Total'
 
-# Combine the total row with the data frame
+## Combine the total row with the data frame
 categorized_data <- bind_rows(categorized_data, total_row_df)
 
-# Select the top 5 rows for display
+## Select the top 5 rows for display
 categorized_data_top5 <- head(categorized_data, 5)
 
-# Create the table with kable and kableExtra, displaying only the top 5 rows
+## Create the table with kable and kableExtra, displaying only the top 5 rows
 categorized_data_table <- categorized_data_top5 %>%
   select(year, everything()) %>% # Ensure the 'year' column is first
   kable("latex", row.names = FALSE, booktabs = TRUE) %>%  # Use LaTeX format for PDF
@@ -72,11 +72,11 @@ categorized_data_table <- categorized_data_top5 %>%
   row_spec(0, bold = TRUE) %>%  # Make the header row bold
   column_spec(1, bold = TRUE)  # Make the first column bold
 
-# Print the table
+## Print the table
 categorized_data_table
 
 
-## Trends in Public Opinion Over Time in The US
+# Trends in Public Opinion Over Time in The US
 ggplot(total_responses_per_year, aes(x = year, y = total_responses)) +
[…]

### 2024-04-20 scripts/04-model.R
Update model

@@ -12,13 +12,13 @@ library(rstanarm)
 library(arrow)
 
 #### Read data #### -- put this section into cleaning "additional data set for model"
-too_little_data <- read_csv("~/Welfare and The Economy/data/analysis_data/too_little_data.csv")
+model_data <- read_csv("~/Welfare and The Economy/data/analysis_data/model_data.csv")
 
 ### Model data ####
 first_model <-
   stan_glm(
     formula = total_responses ~ year,
-    data = too_little_data,
+    data = model_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-04-20 other/datasheet/datasheet.qmd
Update datasheet

@@
 If so, please provide a description.*
-	- No
+	- The dataset does not contain any information that could be considered confidential. It consists of aggregated responses without any personal identifiers.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- No
+	- The dataset is composed of statistical data regarding public opinion on welfare and does not contain any content that could be deemed offensive, insulting, threatening, or likely to cause anxiety.
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- No
+	- The dataset does not identify any sub-populations by age, gender, or other demographic factors.
+It is purely an aggregation of responses categorized as "Too Little," reflecting public opinion on welfare adequacy.
 14.
@@
 If so, please describe how.*
-	- No
+	- It is not possible to identify individuals directly or indirectly from the dataset. The responses are anonymized and aggregated to ensure privacy and confidentiality.
 15.
@@
 If so, please provide a description.*
-	- No
+	- The dataset does not contain any sensitive data.
+It is limited to general perceptions of welfare provisions without revealing any race, ethnic origins, sexual orientations, religious beliefs, political opinions, or any other personal information.
 16. *Any other comments?*
@@
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- No.
+	- The dataset is not a sample but represents the complete set of responses classified as "Too Little" regarding welfare adequacy from the General Social Survey (GSS) across specified years.
+This comprehensive data collection aims to reflect general trends without implementing a sampling strategy.
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- Broad groups from the public.
+	- The data collection was conducted as part of the General Social Survey, which involves broad groups from the public participating in the surveys.
+These participants are not typically compensated as the GSS is a standard sociological survey designed to collect general societal metrics.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- No.
+	- The data was collected from 1972 to 2022, annually.
+Each dataset corresponds to the responses gathered within that year, directly reflecting the public opinion of that time without retrospective compilation.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- No.
+	- The General Social Survey, from which this dataset is derived, adheres to ethical standards typical of sociological research.
+However, specific details on the ethical review processes for this dataset were not disclosed in the documentation available.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- No.
+	- Data was collected directly from individuals through structured survey methodologies employed by the General Social Survey, without intermediary third parties.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- No.
+	- Participants in the General Social Survey are typically notified about the data collection at the time of the survey, as part of the survey’s introduction and consent process, which informs participants of the study's nature, purpose, and use of the data collected.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- No.
+	- Yes, consent is obtained from all participants in the GSS.
+This consent is typically verbal and given in response to a standard set of introductory remarks explaining the survey's purpose and use of the information collected.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- No.
+	- The General Social Survey procedures include provisions for participants to revoke their consent regarding the use of their data in future studies.
+Details on the mechanism for revocation are usually outlined in the participant information sheet provided during the survey.
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- No.
+	- There is no specific documentation of a data protection impact analysis for this dataset.
+Typically, the GSS employs general privacy protection and data usage policies that comply with sociological research standards to mitigate potential adverse impacts on participants.
 12. *Any other comments?*
@@
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- No.
+	- There is currently no central repository linking to all papers or systems that use this dataset. The dataset is primarily utilized internally by the research team for socio-economic analyses.
 3. *What (other) tasks could the dataset be used for?*
-	- No.
+	- Beyond analyzing public opinion trends, the dataset could potentially be used for comparative studies on socio-economic conditions over time, training predictive models for social policy forecasting, or cross-referencing with other socio-economic data to examine broader impacts of welfare perceptions.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- No.
+	- Consumers of the dataset should be aware that it exclusively contains responses categorized as "Too Little," which might skew perceptions if not properly contextualized within broader research.
+To mitigate potential biases and ensure fair analysis, users should consider integrating this dataset with broader datasets covering various response categories.
+The dataset’s focus on aggregated survey responses means it lacks individual-level data, which could limit detailed demographic analyses unless supplemented with additional data sources.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- No.
+	- This dataset should not be used for tasks that require individualized data or detailed demographic insights, such as personalized service delivery or targeted interventions, without additional, supplementary data to provide those details.
+It is also not suitable for predictive tasks without proper contextualization and validation against more comprehensive datasets.
 6. *Any other comments?*
@@
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- N/A
+	- The dataset is not publicly distributed via common data sharing platforms such as tarballs on websites, APIs, or GitHub, and it does not have a Digital Object Identifier (DOI).
+Access is restricted to the research team and specific academic collaborators under controlled conditions to maintain the integrity and confidentiality of the data.
 3. *When will the dataset be distributed?*
-	- N/A
+	- There are no plans for public distribution of the dataset. Distribution is limited to internal use within the research institution and its direct academic partners.
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- N/A
+	- Since the dataset is not publicly distributed, it does not come under any specific copyright or IP license for external users.
+Within the research institution, it is governed by internal data use agreements that prescribe how the data can be used, shared, and referenced in publications.
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- N/A
+	- No third-party IP-based or other restrictions are imposed on the dataset.
+All data used and generated from the General Social Survey (GSS) comply with the survey’s terms of use, which are designed to protect participant confidentiality and the ethical use of the data.
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- N/A
+	- The dataset is not subject to any export controls or regulatory restrictions due to its nature (aggregated and anonymized data) and the scope of use (academic and research purposes within the United States).
+The data handling and use comply with all applicable U.S.
+regulations regarding research data.
 7. *Any other comments?*
@@
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- N/A
+	- The dataset is managed by the research team at the academic institution that compiled it.
+For inquiries or further information, contact can be made through the institution’s main communication channels provided on their website or directly through the research department's email, typically available in the public domain or through academic publications.
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- N/A
+	- Currently, there are no known errors reported that would require publishing an erratum.
+Should any issues be identified, necessary corrections will be made and communicated through the appropriate academic channels and updated in the dataset documentation.
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- N/A
+	- The dataset is subject to updates to correct any identified errors, add new instances from subsequent GSS surveys, or delete instances if found incorrect.
+Updates are planned on an annual basis following the release of new GSS data.
+The research team will manage updates, and notifications of these updates will be communicated to dataset users via academic publications and announcements on relevant research forums.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- N/A
+	- The data is retained in line with ethical guidelines and institutional policies regarding data privacy and retention.
+Typically, data from surveys like the GSS are retained as long as they are relevant for research purposes and are destroyed in accordance with the data retention policy of the institution once they are no longer needed.
+This ensures compliance with legal and ethical standards.
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- N/A
+	- Older versions of the dataset will be maintained alongside the most current version to ensure historical comparability and continuity in longitudinal studies.
+Information regarding any changes, including the retirement of older datasets, will be clearly communicated to users through the institution’s research communication channels.
 7.
@@
 If so, please provide a description.*
-	- N/A
+	- While the main dataset is tightly controlled by the original research team, contributions in terms of secondary analysis, derived datasets, or suggestions for improvement are welcome.
+Contributors can submit their proposals or derived data through a formal submission process managed by the research team.
+All contributions will be reviewed for accuracy and relevance before integration or acknowledgment.
+Details of this process are available upon request and are typically outlined in the dataset’s governance documentation.
 8. *Any other comments?*

### 2024-04-23 paper/paper.qmd
Update figure 1

@@
 abstract: "A country's economic conditions often influence public perceptions of government welfare practices.
-However, do all citizens truly meet the general expectation of higher welfare during economic downturns and higher welfare during economic boom?
+However, do all citizens truly meet the general expectation of higher welfare during economic downturns and lower welfare during economic boom?
 Using data from the General Social Survey (GSS) Welfare, this paper examines whether the American public believes government welfare initiatives have been adequate over the past 50 years, particularly under different economic circumstances.
 Our analysis shows that there are widespread public calls to reduce welfare spending during good times, while in bad times, this leads to a stronger demand for government assistance.
-Despite this trend, journal research shows that differences in welfare expectations remain evident between different demographic groups, such as high- and low-income groups.
+Despite this trend, journal research shows that differences in welfare expectations remain evident between different demographic groups, such as high and low-income groups.
 This finding highlights the need for society to develop welfare policies for different groups and provide a basis for creating fairer and more sensitive welfare strategies amid economic fluctuations."
@@
 Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns.
-This study investigates whether there's a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession, the 2008 Global Financial Crisis, and the 2020 COVID-19 pandemic.
+This study investigates whether there is a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession and the 2020 COVID-19 pandemic.
 Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups through various journal research.
@@
 This is assessed through the lens of varying response groups to understand if the demand for greater welfare support is a ubiquitous response to economic hardship.
-Our preliminary findings reveal that public opinion is actually multifaceted.
+Our preliminary findings show that public opinion is multifaceted.
 The recession significantly affected demand for increased government welfare action but with significant differences across demographic groups; different incomes or other social factors will significantly affect people's views on welfare.
@@
 The subsequent [Data] section outlines our methods and data-cleaning efforts.
-In the [Model] section, we use a linear regression model to further analyze the number of public responses to "Too Little" of welfare since 1972.
+In the [Model] section, we use a linear regression model to further analyze the number of public responses to "too little" of welfare since 1972.
 The [Results] section presents findings on public welfare perceptions under different economic conditions.
@@
 Survey Audience GSS focuses on adults 18 years of age and older who live in the United States and communicate in English or Spanish [@gssCodebook2022].
-We worry that despite this inclusion criterion enabled a more diverse group of participants to contribute to the survey.
-However, those who do not meet these language requirements or are still unable to participate for health reasons are excluded from the scope of the @GSS.
+We worry that despite this inclusion criterion enabled a more diverse group of participants to contribute to the survey; those who do not meet these language requirements or are still unable to participate for health reasons are excluded from the scope of the @GSS.
 
@@
 Screening analyses form another key component of our statistical analysis.
-By classifying years according to the extreme sentiment expressed about welfare spending, we identify periods particularly salient in public opinion (e.g., unusually high levels of a certain variable).
+By classifying years according to the extreme sentiment expressed about welfare spending, we identify periods particularly salient in public opinion (e.g.
+unusually high levels of a certain variable).
 This approach allows us to isolate and examine years of significant public consensus on welfare policy and compare it to years of average economic growth to understand the potential catalysts driving these sentiments.
@@
 Overall, despite these fluctuations, there is a discernible upward trend in the recent 10 years (2012-2022), culminating in a prominent peak towards the end of the period under consideration.
-This trend suggests an increasing number of respondents perceive welfare provisions to be inadequate in more recent years.
+This trend shows an increasing number of respondents perceive welfare provisions to be inadequate in more recent years.
 
@@
 Our data analysis found trends in the “too little” category of General Social Survey responses that could indicate public perceptions of benefit adequacy.
-This trend corresponds to the changing economic landscape over the years, and to capture this dynamic quantitatively, we designed a linear regression model to predict the likelihood of a “too few” response depending on the year of survey.
+This trend corresponds to the changing economic landscape over the years, and to capture this dynamic quantitatively, we designed a linear regression model to predict the likelihood of a “too little” response depending on the year of survey.
 We ran the model in R [@citeR] using @rstanarm's `rstanarm` package.
@@
 We posit a clear relationship between the passage of time and the rising public advocacy for more comprehensive welfare reflected in "too little" responses within the General Social Survey (GSS) data.
-Specifically, we hypothesize that the proportion of "Too Little" responses exhibits a consistent upward trend from 1972 to 2022, indicative of a growing public sentiment that government welfare provision is falling short of societal needs.
+Specifically, we hypothesize that the proportion of "too little" responses exhibits a consistent upward trend from 1972 to 2022, indicative of a growing public sentiment that government welfare provision is falling short of societal needs.
 
 The linear regression model we propose serves to validate this hypothesis mathematically.
-If the coefficient $\beta_1$ to be positive will confirm our assumption of an upward trajectory for “too few” responses.
-As an illustrative example, suppose that the GSS data show a large increase in “too few” responses in the years following the implementation of the welfare reform policy, which would appear in our model as a steeper slope in these years.
+If the coefficient $\beta_1$ to be positive will confirm our assumption of an upward trajectory for “too little” responses.
+As an illustrative example, suppose that the GSS data show a large increase in “too little” responses in the years following the implementation of the welfare reform policy, which would appear in our model as a steeper slope in these years.
 
@@
 The linear model outlined in @tbl-linear-trend and visualized in the accompanying graph suggests a positive trend in the frequency of "too little" responses over the surveyed years.
-This trend is evidenced by the positive coefficient for 'year' ($\beta_1$ = 3.63), which suggests that each successive year is associated with a slight increase in the proportion of "Too Little" responses.
+This trend is evidenced by the positive coefficient for 'year' ($\beta_1$ = 3.63), which suggests that each successive year is associated with a slight increase in the proportion of "too little" responses.
 
@@
 ## Model Limitations
-The Model section introduces a linear regression model to predict the probability of a "Too Little" response based on the survey year.
+The Model section introduces a linear regression model to predict the probability of a "too little" response based on the survey year.
 While the model's simplicity is a strength, it's also a limitation.
@@
 Other potential predictors, such as unemployment rates, economic growth indicators, or significant political events, are not included in the model but could provide additional explanatory power.
-For example, a year with significant job growth might see a disproportionate decrease in "Too Little" responses, which would not be accounted for by the year alone.
+For example, a year with significant job growth might see a disproportionate decrease in "too little" responses, which would not be accounted for by the year alone.
 

### 2024-04-24 scripts/00-simulate_data.R
Update simulate data

@@ -1,40 +1,58 @@
 #### Preamble ####
 # Purpose: Simulates number of reports in different amount of hours working
 # Author: Tianen (Evan) Hao
-# Date: 14 March 2023 
+# Date: 29 March 2023 
 # Contact: evan.hao@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: none
 
-#### Workspace setup ####
+# Workplace setup and Load necessary libraries
 library(tibble)
 library(dplyr)
-library(tidyr)
+library(ggplot2)
 
-#### Simulate data ####
-# Define years and work hours categories
+# Define the years and categories for responses
+years <- seq(1972, 2022, by = 2)  # Every two years from 1972 to 2022
+response_types <- c("Too Little", "About Right", "Too Much")
 
-# Some of the years are not included due to the fact that many years are
-# missing from the GSS data set
-years <- c(1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 
-           2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 
-           2018, 2021, 2022)
-work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
+# Set seed for reproducibility
+set.seed(123)
 
-# Simulate data
-set.seed(123) # For reproducibility
-simulated_data <- tibble(year = rep(years, each = length(work_hours_categories)),
-                         work_hours = rep(work_hours_categories, times = length(years)),
-                         value = runif(n = length(years) * length(work_hours_categories), min = 50, max = 2000))
+# Create a tibble with simulated data
+simulated_data <- expand.grid(year = years, response_type = response_types) %>%
+  mutate(count_responses = runif(n = n(), min = 100, max = 1000))  # Random counts between 100 and 1000
 
-# Pivot to wide format
+# View the first few rows of the simulated data
+head(simulated_data)
+
+# Pivot data to wide format
 simulated_data_wide <- simulated_data %>%
-  pivot_wider(names_from = year, values_from = value)
+  pivot_wider(names_from = response_type, values_from = count_responses)
 
-# Round the values to remove decimals
+# Round the values to make them easier to read
 simulated_data_wide <- simulated_data_wide %>%
-  mutate(across(-work_hours, round))
+  mutate(across(.cols = starts_with("Too"), .fns = round))
 
-# Check the range for a specific year (e.g., 2022)
[…]

### 2024-04-24 paper/paper.qmd
Update figure 1
Update caption for figures

@@
 In this model, proportion\_too\_little_i indicates the predicted proportion of "too little" responses for the i^{th} year, $\beta_0$ represents the model's intercept—the starting point on the y-axis when the year is zero, which we interpret as the survey's baseline year of 1972.
-The coefficient $\beta_1$ indicates the amount of change in "Too Little" responses we can expect with each passing year.
+The coefficient $\beta_1$ indicates the amount of change in "too little" responses we can expect with each passing year.
 If $\beta_1$ is positive, it supports our hypothesis of an upward trend.
@@
 The slight upward trajectory observed in the model output [@tbl-linear-trend] can be interpreted as a growing public sentiment that welfare provision is "too little." This might reflect an overall increase in public expectations for welfare support, possibly driven by social, economic, or policy changes over time.
-The pattern could also indicate a responsiveness to economic conditions, with higher "Too Little" responses potentially following economic downturns.
+The pattern could also indicate a responsiveness to economic conditions, with higher "too little" responses potentially following economic downturns.
 
@@
 #| warning: false
-#| tbl-cap: Linear model showing the trend of Too Little responses
+#| tbl-cap: Linear Model Showing the Trend of Too Little Responses
 #| label: tbl-linear-model
@@
 #| label: tbl-linear-trend
-#| tbl-cap: The model trend of Too Little responses is increasing every years
+#| tbl-cap: The Model Trend of Too Little Responses is Increasing Every Year
 
@@
 #| label: fig-linear-trend
-#| fig-cap: The trend of Too Little responses is increasing every years
+#| fig-cap: The Trend of Too Little Responses is Increasing Every Year
 # Visualizing the trend
@@
 #| warning: false
-#| fig-cap: Comparison between 1980 and 1982, 2018 and 2021
+#| fig-cap: Comparison Between 1980 and 1982, 2018 and 2021
 #| label: fig-comparison-years
@@
 
-## Trends in 'Too Much' Responses
+## Trends in Too Much Responses
 
@@
 #| warning: false
-#| fig-cap: There are major social events in some missing years 
+#| fig-cap: There are Major Social Events in Some Missing Years 
 #| label: fig-missing-years
@@
 #| warning: false
-#| fig-cap: Annual trends show inconsistent total response rates
+#| fig-cap: Annual Trends Show Inconsistent Total Response Rates
 #| label: fig-trends-response
@@
 It may not accurately forecast future trends, especially in the face of unprecedented events such as the COVID-19 pandemic.
-The 2021 spike in "Too Little" responses could be an outlier due to the pandemic's unique economic impact, which a model based on past data might not predict accurately.
+The 2021 spike in "too little" responses could be an outlier due to the pandemic's unique economic impact, which a model based on past data might not predict accurately.
 
@@
 #| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-cap: "Examining How the Model Fits, and is Affected by, the Data"
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-cap: "Checking the Convergence of the MCMC Algorithm"
 #| fig-subcap: ["Trace plot", "Rhat plot"]

### 2024-04-24 paper/paper.qmd
Update caption for figures

@@
 #| warning: false
-#| fig-cap: Trend of Average Inapplicable Responses Per Decade is increasing
+#| fig-cap: Trend of Average Inapplicable Responses Per Decade is Increasing
 #| label: fig-inapplicable-years

### 2024-04-24 paper/paper.qmd
Update structure in introduction

@@
 Public attitudes towards government welfare programs fluctuate with economic conditions, swinging from calls for austerity during prosperous times to demands for increased support in downturns.
-This study investigates whether there is a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there's a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession and the 2020 COVID-19 pandemic.
+This study investigates whether there is a consistent trend of advocating for reduced welfare spending in periods of economic prosperity and whether there is a noticeable shift towards supporting more government welfare provisions during downturns, as seen during the 1982 recession and the 2020 COVID-19 pandemic.
 Importantly, we explore whether this trend is consistent across all public segments or if attitudes vary among different demographic groups through various journal research.
@@
 The subsequent [Data] section outlines our methods and data-cleaning efforts.
-In the [Model] section, we use a linear regression model to further analyze the number of public responses to "too little" of welfare since 1972.
+In the [Model] section, we use a linear regression model to further analyze the number of public responses to "too little" welfare since 1972.
 The [Results] section presents findings on public welfare perceptions under different economic conditions.
-In [Discussion], we interpreted within the larger context of welfare policy and public expectations and are expected to trigger reflections on the study's limitations and potential directions for future research.
+In [Data and Model Limitations] we mainly explain the immature aspects of data and models for analysis results.
+In [Discussion], we interpreted within the larger context of welfare policy and public expectations to reflect on the study's limitations and potential directions for future research.
 Finally, we synthesize our main insights in [Conclusion] to highlight the urgent need for nuanced and adaptable welfare policies.
@@
 We will also give examples of some specific years for analysis, including 1980, 2018, the normal economic years, and 1982, 2021, the years when recession occurred.
-\break
 

### 2024-04-24 scripts/03-test_data.R
Update test data

@@ -9,14 +9,14 @@
 # 01-data_cleaning.R
 
 #### Workspace setup ####
+# Load necessary library
 library(dplyr)
-library(here)
-
 #### Test data ####
 data <- read.csv(here::here("Welfare and The Economy/data/analysis_data/cleaned_data.csv"))
 
-# 1. Verify that all reported welfare perceptions are non-negative
-test_non_negative <- all(select(data, -c(year, AGE, SEX)) >= 0)
+# 1. Verify that all reported welfare responses are non-negative
+# Assuming that the perceptions are stored in columns named after each perception category
+test_non_negative <- all(select(data, starts_with("response")) >= 0)
 print(paste("Test non-negative values: ", test_non_negative))
 
 # 2. Verify that response categories are as expected
@@ -28,29 +28,23 @@ print(paste("Test response categories match: ", test_response_categories))
 test_no_missing_values <- all(!is.na(data$response) & !is.na(data$year))
 print(paste("Test no missing values: ", test_no_missing_values))
 
-# 4. Check for valid age range (assuming 18-99 as a reasonable range)
-test_valid_ages <- all(data$AGE >= 18 & data$AGE <= 99)
-print(paste("Test valid age range: ", test_valid_ages))
+# 4. Check for valid year range (assuming 1972-2022 as a reasonable range)
+test_valid_years <- all(data$year >= 1972 & data$year <= 2022)
+print(paste("Test valid year range: ", test_valid_years))
 
-# 5. Check for consistent gender data
-expected_genders <- c("MALE", "FEMALE")
-test_gender_data <- all(data$SEX %in% expected_genders)
-print(paste("Test gender consistency: ", test_gender_data))
-
-# 6. Ensure year column covers the correct range
-test_correct_year_range <- min(data$year) >= 1972 & max(data$year) <= 2024
+# 5. Ensure the 'year' column covers the correct range
+test_correct_year_range <- min(data$year) >= 1972 & max(data$year) <= 2022
 print(paste("Test correct year range: ", test_correct_year_range))
 
-# 7. Check that each year has a plausible number of responses (for simulation purpose)
+# 6. Check that each year has a plausible number of responses (for simulation purpose)
 # Assuming an expected minimum and maximum number of responses per year
 min_responses <- 100  # Minimum expected responses
 max_responses <- 1000  # Maximum expected responses
 test_year_responses <- all(data$response_count >= min_responses & data$response_count <= max_responses)
 print(paste("Test year responses in range: ", test_year_responses))
 
[…]

### 2024-04-24 scripts/05-data_tabling.R
Update data tabling

@@ -250,7 +250,7 @@ kable(
 ) %>%
   kable_styling(bootstrap_options = c("striped", "hover"))
 
-# Trends in About Right Responses
+# Trends in Too Much Responses
 
 library(ggplot2)
 library(dplyr)
